### 2025-02-25 manuscript.qmd
Manuscript document created

---
title: "manuscript"
format: pdf
editor: visual
---

## Quarto

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

### 2025-02-26 data/preparation.Rmd
updating data preparation

---
title: "preparation"
author: "Reilly Amera"
date: "2025-02-26"
output: html_document
---

```{r setup}
library(tidyverse)
```

```{r read-in}
child <- read_csv("child.csv", col_names = TRUE)
parent <- read_csv("parent.csv", col_names = TRUE)
```

```{r cleaning}
# removing unnecessary columns
child <- child %>% 
  select(-c(1:5, 8:18))
child <- child[-c(1, 2),]

parent <- parent %>% 
  select(-c(1:6, 8:18))
parent <- parent[-c(1, 2),]

# replacing one NA (participant forgot ID)
child$PID[is.na(child$PID)] <- 1

# renaming 'finished' columns 
child <- child %>% 
  rename(Cfinished = Finished)

parent <- parent %>% 
  rename(Pfinished = Finished)
```

```{r wrangling}
# merging datasets
youtube <- full_join(parent, child, by = "PID")

# removing instances where either parents or children failed to finish
youtube <- youtube %>% 
  filter(Pfinished == Cfinished)
```

### 2025-02-26 manuscript.qmd
Updated citations

@@
 ---
-title: "manuscript"
+title: "YouTube Kids: The Effect of YouTube on Children’s Racial Learning"
+shorttitle: "YouTube Racial Attitudes"
+author: 
+- name: Reilly Amera
+  corresponding: true
+  email: ramera@uchicago.edu
+  affiliations:
+  - id: id1
+    name: "University of Chicago"
+    department: MA Program in the Social Sciences
+bibliography: [r-references, bibliography.bib]
 format: pdf
@@
 
-## Quarto
+```{r}
+#| label: setup
+#| include: false
 
-Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.
+library(papaja)
+library(knitr)
+library(broom)
+library(tidyverse)
 
-## Running Code
+# Generate or overwrite r-reference files
+r-refs("r-references.bib")
+```
 
-When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:
+## Introduction
+
+Is YouTube making kids more racist?
+Despite sounding like the cultural fear-mongering often associated with screen time and development, such a question refers to real concerns that psychological research has yet to address: what are children really learning from YouTube, particularly with regard to race?
+
+### Literature Review {#sec-lit-review}
+
+Much of the literature on how children learn about their racial world places great emphasis on the transmission of information that is explicitly about race: how parents talk about members of other racial groups, how and whether schools portray the histories of marginalized groups, how peers may communicate stereotypes, etc.
+[@hugheswatford_2022_racial].
+In this view, ethnic-racial socialization, or the ways in which agents transmit messages about ethnicity and race to children, occurs through direct verbal instruction.
+However, in addition to more explicit transmissions of racial knowledge, children are simultaneously exposed to a barrage of more implicit environmental inputs—who they live near, for instance, or who they see on screens—which may also affect these conceptions [@hughesetal_2023_growing].
+Not only does ethnic-racial socialization occur with explicit instruction, but so too do children attend to the racial patterns and organizations embedded into their environments and social settings [@hugheswatford_2022_racial].
+Such environmental racial patterns—who tends to hold positions of authority, who tends to receive discipline in school, etc.—constitute racial regularities, or “persistent patterns in the relative social experiences of, or roles occupied by, two or more racial (or racialized groups) within a setting”  [@hugheswatford_2022_racial].
+In response to such patterns, children engage in racial learning, or the meaning-making of external messaging so as to form their own conceptions of how race works in their social world [@hugheswatford_2022_racial].
+As such, when exposed to consistent, repeated regularities, children draw inferences as to why such patterns exist and persist; they may accept that such patterns as necessary features of ‘the way things are,’ or may even create explanations for such patterns (e.g.
+“White families live in big houses because they work hard” in contrast to “Black families live in big houses because they got lucky”) [@hughesetal_2023_growing; @rizzoetal_2022_beliefs].
+Further, this learning may be yet more implicit: when tested in the same environment, young children show levels of implicit biases, unconscious mental associations based on race or other social categories, similar to those of adults [@payneetal_2017_bias].
+This suggests that features of specific environments such as racial regularities not only affect explicitly articulated beliefs but implicit understandings of one’s social environment.
+As such, to fully understand how children’s conceptions of race form, we must examine the ways in which environments containing ontologically inaccurate racial regularities affect their racial learning.
+One such environmental stream of input regarding race and racial regularities is social media.
+Children today have unparalleled access to social media platforms: YouTube, TikTok, Twitch, and more.
+On these sites, the sheer amount of content posted often outpaces enforcement of content guidelines, making it difficult to know exactly what children are seeing or learning from the content they are consuming.
+Unlike media such as television or movies, social media platforms are populated by both media corporations and individual content creators.
+YouTube is a social media platform that is particularly popular amongst children; many children use YouTube regularly: one third of parents of children aged 11 and younger surveyed by Pew Research Center indicated that they let their children use YouTube regularly [@smithetal_2018_many].
+Further, amongst tweens and teens, video logs and gaming videos—types of content usually generated by influencers, not corporations—are the two most popular genres watched [@rollinsetal_2022_who].
+Despite massive popularity, research on the effects of YouTube and other forms of social media on children’s race-related attitudes and behaviors has not been methodologically systematic [@wardbridgewater_2023_media].
+Though YouTube has become a regular part of children’s lives, it is still unknown how YouTube may be affecting children’s conceptions of racial categories and associated beliefs about race.
+However, some research has emerged describing racial regularities on YouTube: in a review conducted by Common Sense Media, in YouTube videos watched by children under the age of 8, prominent characters of color were far more likely to engage in violent behaviors or inappropriate language, and were less likely to appear alongside educational content [@rollinsetal_2022_who].
+In another content analysis of the most popular YouTube videos at the time, more than three-fifths of videos in the sample included racial stereotypes, most of which reinforced and perpetuated them [@guoharlow_2014_usergenerated].
+Taken together, we see that YouTube contains racial regularities in the form of stereotypes, which children may be accommodating into their beliefs, but there has not yet been any research confirming this connection.
+While there is a body of research aimed at understanding how certain aspects of children’s environments contribute to the formation of racial attitudes, there is not as much focus on how YouTube, or other social media platforms, function as sites of racial socialization and learning via racial regularities.
+Similarly, though there have been some content analyses regarding the racial character of YouTube videos, such studies have yet to be done in conjunction with psychological measures of racial beliefs and attitudes.
+Due to this lack of research into how social media ecologies contribute to kids’ racial beliefs, I thus ask the question: are children for whom stereotypical social media is a part of their daily environment more likely to develop stereotyping or prejudicial racial beliefs and attitudes?
+
+### Present Study {#sec-present-study}
+
+This study will examine the relationship between YouTube usage and children’s development of racial attitudes, so as to understand whether and the degree to which YouTube may be a site of ethnic-racial socialization where children develop prejudices against those of other races.
+I hypothesize that time spent on YouTube and children’s observation of racial regularities should covary; as children spend more time on YouTube, they may observe more negatively valenced racial regularities including people of color [@guoharlow_2014_usergenerated; @rollinsetal_2022_who].
+Thus, I hypothesize that if children spend more time on YouTube, they will display greater racial stereotyping and prejudice against outgroups.
+While some children may not be consciously aware of on-screen racial regularities, these dynamics may still affect their racial attitudes [@hugheswatford_2022_racial].
+As such, I hypothesize that the relationship between children’s time spent on YouTube and their exhibited racial stereotyping and prejudice will be mediated by their observations of negative racial regularities.
+One additional factor that may moderate the relationship between time spent on YouTube and racial attitudes is whether a child’s favorite YouTuber is of a race other than their own, via the parasocial contact hypothesis.
+This theory suggests that when individuals have limited real life interpersonal contact with minority groups, the formation of parasocial (one-sided) relationships with outgroup media figures may reduce stereotyping and prejudice [@schiappaetal_2005_parasocial; @wongetal_2022_theorizing].
+Much of the parasocial contact hypothesis literature explores the prejudice reduction made possible by parasocial relationships with television characters, yet the growing popularity of social media presents another medium through which parasocial relationships may be formed.
+If positive parasocial contact hypothesis effects may be observed when individuals form relationships with characters in other media, so too should these effects be observed when individuals have parasocial relationships with outgroup influencers [@banasetal_2020_metaanalysis].
+Thus, I pose my third hypothesis: the relationship between the amount of time that children spend on YouTube and their racial stereotyping and prejudice will be moderated by whether they have a parasocial relationship with a favorite YouTuber of a race other than their own.
+Specifically, if children have a favorite YouTuber of a race other than their own and they have a parasocial relationship with this YouTuber, they will display less racial stereotyping and prejudice.
 
 ```{r}
-1 + 1
+#| label: data analysis
+#| echo: false
+# FOR THIS DRAFT - only include child data and simple regressions 
 ```
 
-You can add options to executable code like this
-
-```{r}
-#| echo: false
-2 * 2
-```
-
-The `echo: false` option disables the printing of code (only output is displayed).
+# References
+::: {#refs}
+:::

### 2025-02-27 data/preparation.Rmd
Data preparation updated

@@
 ```{r setup}
+library(eeptools)
 library(tidyverse)
@@
   select(-c(1:6, 8:18))
-parent <- parent[-c(1, 2),]
+parent <- parent[-c(1),]
 
@@
   rename(Pfinished = Finished)
+
+# Will need to clean parent reported time data. Did so out of R for this draft, but will do it in R for the final version of this project. Find the unedited version in localonly
 ```
@@
 youtube <- youtube %>% 
-  filter(Pfinished == Cfinished)
+  filter(Pfinished == Cfinished) %>% 
+  # excluding attention check question for now
+  select(-c(`homophily-behave_5`))
+
+# create age column
+# used YouTube (funny right?)
+date_today <- Sys.Date()   # Current date
+youtube <- youtube %>% 
+  mutate(bday = as.Date(bday, format = "%m/%d/%Y")) %>% 
+  mutate(age = age_calc(
+    bday,
+    date_today,
+    units = "years"
+  ))
+
+# merge genre and genre_8_TEXT - replace 'other' with the entry
+
 ```
+
+```{r wrangling}
+# CATEGORICAL: Dealing with Likert scales - child survey items
+
+# QUESTION: DO I KEEP THIS DATA ORDINAL OR TURN IT NUMERIC?
+
+# Making relevant items into factors and creating levels 
+youtube <- youtube %>% 
+  # days
+  mutate(days = as_factor(days)) %>% 
+  mutate(days = fct_relevel(days, c("Never", 
+                "1 to 2 days a week",
+                "3 to 4 days a week",
+                "5 to 6 days a week",
+                "Every day"))) %>% 
+  # Ctime
+  mutate(Ctime = as_factor(Ctime)) %>% 
+  mutate(Ctime = fct_relevel(Ctime, c("About 15 minutes a day", 
+                "About 30 minutes a day",
+                "About 45 minutes a day",
+                "About 1 hour a day",
+                "About 1 and 1/2 hours a day",
+                "More than 2 hours"))) %>% 
+  # malleable and behavior
+  mutate(
+    across(c(malleable_1, malleable_2, malleable_3, malleable_4, behavior_1, behavior_2, behavior_3, behavior_4, behavior_5, behavior_6, behavior_7),
+           ~ fct_relevel(as_factor(.),
+             "Strongly disagree",
+             "Somewhat disagree",
+             "Neither agree nor disagree",
+             "Somewhat agree",
+             "Strongly agree"
+           ))) %>% 
+  # homophily and parasocial 
+  mutate(
+    across(c(`homophily-appear_1`, `homophily-appear_2`, `homophily-appear_3`, `homophily-appear_4`, `homophily-appear_5`, `homophily-behave_1`, `homophily-behave_2`, `homophily-behave_3`, `homophily-behave_4`, `homophily-behave_6`, parasocial_1, parasocial_2, parasocial_3, parasocial_4, parasocial_5),
+           ~ fct_relevel(as_factor(.),
+             "Really disagree",
+             "Disagree",
+             "I don't know",
+             "Agree",
+             "Really agree"
+           )))  %>% 
+  # outgroup-freq
+  mutate(`outgroup-freq` = as_factor(`outgroup-freq`)) %>% 
+  mutate(`outgroup-freq` = str_trim(`outgroup-freq`)) %>% 
+  mutate(`outgroup-freq` = fct_relevel(`outgroup-freq`, c("Never",
+                "Rarely",
+                "Sometimes",
+                "Often",
+                "Very often")))
+
+# not including outgroup-simple for now
+```
+
+```{r}
+# NUMERIC - Dealing with Likert scales - child survey items
+
+# Making relevant items numeric 
+youtube <- youtube %>% 
+  # malleable and behavior
+  mutate(
+    across(c(malleable_1, malleable_2, malleable_3, malleable_4, behavior_1, behavior_2, behavior_3, behavior_4, behavior_5, behavior_6, behavior_7),
+           ~ recode(.,
+             "Strongly disagree" = 1,
+             "Somewhat disagree" = 2,
+             "Neither agree nor disagree" = 3,
+             "Somewhat agree" = 4,
+             "Strongly agree" = 5
+           ))) %>% 
+  # homophily and parasocial 
+  mutate(
+    across(c(`homophily-appear_1`, `homophily-appear_2`, `homophily-appear_3`, `homophily-appear_4`, `homophily-appear_5`, `homophily-behave_1`, `homophily-behave_2`, `homophily-behave_3`, `homophily-behave_4`, `homophily-behave_6`, parasocial_1, parasocial_2, parasocial_3, parasocial_4, parasocial_5),
+           ~ recode (.,
+             "Really disagree" = 1,
+             "Disagree" = 2,
+             "I don't know" = 0,
+             "Agree" = 3,
+             "Really agree" = 4
+           )))  %>% 
+  # outgroup-freq
+  mutate(`outgroup-freq` = recode(`outgroup-freq`, 
+                "Never" = 1,
+                "Rarely" = 2,
+                "Sometimes" = 3,
+                "Often" = 4,
+                "Very often" = 5))
+```
+
+```{r}
+# Dealing with Likert scales - child survey items
+
+# Composite scores
+# Racial attitudes score -- total possible score = 20
+youtube <- youtube %>% 
+  mutate(malleable_score = rowSums(across(malleable_1:malleable_4))) %>% 
+  mutate(malleable_score = malleable_score/20)
+
+# Parasocial relationship scores (each block separately, then aggregate)
+youtube <- youtube %>% 
+  # homophily-appear -- total possible score = 20
+  mutate(h_appear_score = rowSums(across(`homophily-appear_1`:`homophily-appear_5`))) %>% 
+  # homophily-behave -- total possible score = 20
+  mutate(h_behave_score = rowSums(across(`homophily-behave_1`:`homophily-behave_6`))) %>% 
+  # parasocial -- total possible score = 20
+  mutate(parasocial_score = rowSums(across(parasocial_1:parasocial_5))) %>% 
+  #Composite scores
+  mutate(composite = rowSums(across(h_appear_score:parasocial_score))) %>% 
+  # Proportion scores
+  mutate(h_appear_score = h_appear_score/20) %>%
+  mutate(h_behave_score = h_behave_score/20) %>%
+  mutate(parasocial_score = parasocial_score/20) %>%
+  mutate(composite = composite/60)
+
+# Racial regularities score (behavior) -- total possible score = 35
+youtube <- youtube %>% 
+  # Reverse coded items
+  mutate(across(c(behavior_3, behavior_5, behavior_7), ~ 6 - .)) %>% 
+  # Score
+  mutate(regularity_score = rowSums(across(behavior_1:behavior_7))) %>% 
+  mutate(regularity_score = regularity_score/35)
+
+# definitely need to calculate cronbach's alphas...
+```

### 2025-02-27 manuscript.qmd
Updated manuscript draft

@@
     department: MA Program in the Social Sciences
-bibliography: [r-references, bibliography.bib]
-format: pdf
+bibliography: [bibliography.bib]
+link-citations: true
+draft-date: false
+lang: en
+language:
+  citation-last-author-separator: "and"
+  citation-masked-author: "Masked Citation"
+  citation-masked-date: "n.d."
+  citation-masked-title: "Masked Title"
+  email: "Email"
+format:
+  apaquarto-html: default
+  apaquarto-docx: default
+  apaquarto-typst: 
+    keep-typ: true
+    list-of-figures: true
+    list-of-tables: true
+    toc: true
+  apaquarto-pdf:
+    documentmode: man
+    keep-tex: true
+    list-of-figures: true
+    list-of-tables: true
+    fig-width: 2
+    fig-height: 2
+    out-width: 40%
 editor: visual
@@
 
+library(svglite)
 library(papaja)
@@
 # Generate or overwrite r-reference files
-r-refs("r-references.bib")
+# papaja::r_refs(file = "r-references.bib")
+
 ```
@@
 “White families live in big houses because they work hard” in contrast to “Black families live in big houses because they got lucky”) [@hughesetal_2023_growing; @rizzoetal_2022_beliefs].
-Further, this learning may be yet more implicit: when tested in the same environment, young children show levels of implicit biases, unconscious mental associations based on race or other social categories, similar to those of adults [@payneetal_2017_bias].
-This suggests that features of specific environments such as racial regularities not only affect explicitly articulated beliefs but implicit understandings of one’s social environment.
+Further, this learning may be yet more implicit: when tested in the same environment, young children show levels of implicit biases, unconscious mental associations based on race or other social categories, similar to those of adults [@payneetal_2017_bias] This suggests that features of specific environments such as racial regularities not only affect explicitly articulated beliefs but implicit understandings of one’s social environment.
 As such, to fully understand how children’s conceptions of race form, we must examine the ways in which environments containing ontologically inaccurate racial regularities affect their racial learning.
@@
 
+## Methods {#sec-methods}
+
+### Participants and Procedures {#sec-participants-and-procedures}
+This study will include children between the ages of 8 and 13.
+Though children may express negative racial attitudes prior to this point in development, during early adolescence, children develop the ability to recognize and reflect on the racial patterns and dynamics present in their environments (Hughes & Watford, 2022).
+As such, this age range should allow me to observe how the observation racial regularities present on YouTube may affect children’s stereotyping and prejudicial attitudes, and how such a phenomenon develops.
+Participants will be recruited through Qualtrics Panels, which will allow me to obtain a representative sample of parents and children; other studies have used Qualtrics Panels with similar methods and populations (Byrd & Ahn, 2020).
+Data will be collected during February and March of 2025 from families recruited via Qualtrics Panels.
+Participating families will receive two Qualtrics surveys to be completed asynchronously, and they will receive compensation (around $10-$15; the final amount will be determined by Qualtrics Panels) after both surveys have been completed.
+First, parents will complete a demographics and YouTube usage survey, in which they will answer questions related to parent and child demographics (child age, race/ethnicity, parent income and level of education, etc), as well as questions regarding their child’s YouTube usage (for instance, time spent on YouTube, as reported by their child’s device screen time).
+Then, children will complete their own survey.
+
+### Measures {#sec-measures}
+First, they will answer questions related to their YouTube usage (perceptions of time spent).
+Next, they will either answer more questions pertaining to YouTube content, or their general racial attitudes; either block of questions will appear randomly, so as to reduce the influence of question order.
+In the racial attitudes section, children will answer questions regarding outgroup prejudices, as rated on a Likert scale.
+They will also complete one friend choice item, as a simple exploratory measure of racial preference.
+In the YouTube content section, children will be asked to think of their favorite YouTuber as they answer questions related to whether they have a parasocial relationship with that YouTuber, as well as their observations of racial regularities on YouTube.
+
+## Results {#sec-results}
+
 ```{r}
-#| label: data analysis
+#| label: regression 
 #| echo: false
-# FOR THIS DRAFT - only include child data and simple regressions 
+#| message: false
+#| warning: false
+
+# In the future, will have a final, written out, intermediate dataset that will be read in here.
+
+# regression model
+model <- lm(malleable_score ~ Ptime, data = youtube)
+
+```
+
+```{r}
+#| label: regression-report-functions
+#| echo: false
+#| message: false
+#| warning: false
+
+# report_regression takes a lm model object as an argument
+# and returns a string of format:
+# "$F$(df, df.residual) = F-value, $p$ = p-value, $R^2$ = r-squared"
+report_regression <- function(model) {
+
+  # Extract coefficients and p-values
+  m_glance <- glance(model)
+
+  # Format the p-value
+  p_value <- apa_p(m_glance$p.value, add_equals = TRUE)
+
+  # Create a string with the results
+  report <- paste0("$F$(", 
+                   m_glance$df, 
+                   ", ", m_glance$df.residual, 
+                   ") = ", round(m_glance$statistic, 2), 
+                   ", $p$ = ", p_value, ", $R^2$ = ", round(m_glance$r.squared,2))
+
+  return(report)
+
+}
+
+```
+
+Below is a simple regression displaying the relationship between time spent on YouTube and a child's racial attitudes.
+Despite a visual upward trend, this relationship is not statistically significant: `r report_regression(model)`.
+
+```{r}
+#| label: regression-plot
+#| fig-cap: "Simple Correlation Between Time Spent on YouTube and Racial Attitudes score"
+#| fig-scap: "Time v. Attitudes"
+#| fig-align: "center"
+#| fig-width: 6
+#| fig-height: 4
+#| echo: false
+#| message: false
+#| warning: false
+
+model_plot <- ggplot(youtube) +
+  aes(x = Ptime, y = malleable_score) +
+  geom_point() +
+  stat_smooth(method = "lm") +
+  scale_y_continuous(name = "Racial Attitudes Score") +
+  scale_x_continuous(name = "Time spent on YouTube")
+model_plot
+
 ```
@@
 # References
-::: {#refs}
-:::

### 2025-02-27 data/preparation.Rmd
Updated data preparation
updated data
data preparation updated

@@
 parent <- parent %>% 
-  rename(Pfinished = Finished)
+  rename(Pfinished = Finished) %>% 
+  # ensuring that Ptime is numeric
+  mutate(Ptime = as.numeric(Ptime))
 
@@
 
-```{r wrangling}
+```{r wrangling a}
 # merging datasets
@@
 
-```{r wrangling}
+```{r wrangling b}
 # CATEGORICAL: Dealing with Likert scales - child survey items
@@
 # definitely need to calculate cronbach's alphas...
+
+# temporary intermediate dataset
+write_csv(youtube, "youtube.csv")
 ```

### 2025-02-27 manuscript.qmd
updated manuscript draft
manuscript draft updated
knit/rendered manuscripts
Added some informative comments

@@
 However, in addition to more explicit transmissions of racial knowledge, children are simultaneously exposed to a barrage of more implicit environmental inputs—who they live near, for instance, or who they see on screens—which may also affect these conceptions [@hughesetal_2023_growing].
+
 Not only does ethnic-racial socialization occur with explicit instruction, but so too do children attend to the racial patterns and organizations embedded into their environments and social settings [@hugheswatford_2022_racial].
@@
 As such, to fully understand how children’s conceptions of race form, we must examine the ways in which environments containing ontologically inaccurate racial regularities affect their racial learning.
+
 One such environmental stream of input regarding race and racial regularities is social media.
@@
 Further, amongst tweens and teens, video logs and gaming videos—types of content usually generated by influencers, not corporations—are the two most popular genres watched [@rollinsetal_2022_who].
+
 Despite massive popularity, research on the effects of YouTube and other forms of social media on children’s race-related attitudes and behaviors has not been methodologically systematic [@wardbridgewater_2023_media].
@@
 Taken together, we see that YouTube contains racial regularities in the form of stereotypes, which children may be accommodating into their beliefs, but there has not yet been any research confirming this connection.
+
 While there is a body of research aimed at understanding how certain aspects of children’s environments contribute to the formation of racial attitudes, there is not as much focus on how YouTube, or other social media platforms, function as sites of racial socialization and learning via racial regularities.
@@
 This study will examine the relationship between YouTube usage and children’s development of racial attitudes, so as to understand whether and the degree to which YouTube may be a site of ethnic-racial socialization where children develop prejudices against those of other races.
+
 I hypothesize that time spent on YouTube and children’s observation of racial regularities should covary; as children spend more time on YouTube, they may observe more negatively valenced racial regularities including people of color [@guoharlow_2014_usergenerated; @rollinsetal_2022_who].
@@
 As such, I hypothesize that the relationship between children’s time spent on YouTube and their exhibited racial stereotyping and prejudice will be mediated by their observations of negative racial regularities.
+
 One additional factor that may moderate the relationship between time spent on YouTube and racial attitudes is whether a child’s favorite YouTuber is of a race other than their own, via the parasocial contact hypothesis.
@@
 Participants will be recruited through Qualtrics Panels, which will allow me to obtain a representative sample of parents and children; other studies have used Qualtrics Panels with similar methods and populations (Byrd & Ahn, 2020).
+
 Data will be collected during February and March of 2025 from families recruited via Qualtrics Panels.
@@
 
-# In the future, will have a final, written out, intermediate dataset that will be read in here.
+# BASED ON APAQUARTO DEMO - WILL CHANGE FOR FINAL; WANTED TO TEST RENDERING
+
+# read in data
+youtube <- read_csv("data/youtube.csv", col_names = TRUE)
 
@@
 #| warning: false
+
+# BASED ON APAQUARTO DEMO - WILL CHANGE FOR FINAL; WANTED TO TEST RENDERING AND TRY INLINE REFERENCES
 

### 2025-03-03 manuscript.qmd
updated manuscript

@@
     department: MA Program in the Social Sciences
-bibliography: [bibliography.bib]
+floatsintext: true
+numbered-lines: false
+bibliography: [r-references.bib, bibliography.bib]
 link-citations: true

### 2025-03-07 fake_data/preparation_1.Rmd
Fake data: simulated data

--- 2025-02-27 data/preparation.Rmd
@@
 ```{r setup}
+#install.packages("eeptools") 
+#used for birthday -> age. Found out about this from a YouTube video
 library(eeptools)
 library(tidyverse)
+install.packages("mediation")
+library(mediation)
 ```
@@
              "Disagree" = 2,
-             "I don't know" = 0,
-             "Agree" = 3,
-             "Really agree" = 4
+             "I don't know" = 3,
+             "Agree" = 4,
+             "Really agree" = 5
            )))  %>% 

### 2025-03-08 data/preparation_2.Rmd
Updated data wrangling

---
title: "preparation"
author: "Reilly Amera"
date: "2025-03-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
# Packages
library(tidyverse)
library(eeptools)
```

```{r read-in}
# Read in data
child <- read_csv("child.csv", col_names = TRUE)
parent <- read_csv("parent.csv", col_names = TRUE)
```

```{r cleaning}
# Data Cleaning

# Remove rows that do not contain survey data
parent <- parent[-c(1, 2),]
child <- child[-c(1, 2),]

# Parent cleaning
parent <- parent %>% 
  # remove survey testing responses 
  filter(Q_CHL != "preview") %>% 
  # self consent = agree
  filter(Pconsent_self == "Agree") %>% 
  # child consent = agree
  filter(`Pconsent-child` == "Agree") %>% 
  # remove duplicates
  mutate(Q_RelevantIDDuplicate = 
           # Logical operators
           ifelse(is.na(Q_RelevantIDDuplicate), FALSE, TRUE)) %>% 
  filter(Q_RelevantIDDuplicate != TRUE) %>% 
  # filter attn checks
  filter(yt_opinions_4 == "A lot")

# Child cleaning
child <- child %>% 
  # remove survey testing responses
  filter(Q_CHL != "preview") %>% 
  # consent = yes
  filter(Cconsent == "YES") %>% 
  # filter attn checks 
  filter(homophily_behave_5 == "Agree")

# Remove unnecessary columns
parent <- parent %>% 
  select(-c(StartDate:Q_RelevantIDLastStartDate, gc:tg))
child <- child %>% 
  select(-c(StartDate:UserLanguage, opp, Q_BallotBoxStuffing:tg))

```

```{r merge}
youtube <- inner_join(parent, child, by = join_by(transaction_id))
```

```{r yt-factors}
# CATEGORICAL: Dealing with Likert scales

# Forcats

# Making relevant items into factors and creating levels 
youtube <- youtube %>% 
  # days
  mutate(days = as_factor(days)) %>% 
  mutate(days = fct_relevel(days, c("Never", 
                "1 to 2 days a week",
                "3 to 4 days a week",
                "5 to 6 days a week",
                "Every day"))) %>% 
  # Ctime
  mutate(Ctime = as_factor(Ctime)) %>% 
  mutate(Ctime = fct_relevel(Ctime, c("About 15 minutes a day", 
                "About 30 minutes a day",
                "About 45 minutes a day",
                "About 1 hour a day",
                "About 1 and 1/2 hours a day",
                "More than 2 hours"))) %>% 
  # malleable, regularities, homophily, parasocial
  mutate(
    across(c(malleable_1, malleable_2, malleable_3, malleable_4, regularities_1, regularities_2, regularities_3, regularities_4, regularities_5, regularities_6, regularities_7, `homophily_appear_1`, `homophily_appear_2`, `homophily_appear_3`, `homophily_appear_4`, `homophily_appear_5`, `homophily_behave_1`, `homophily_behave_2`, `homophily_behave_3`, `homophily_behave_4`, `homophily_behave_6`, parasocial_1, parasocial_2, parasocial_3, parasocial_4, parasocial_5),
           ~ fct_relevel(as_factor(.),
             "Really disagree",
             "Disagree",
             "I don't know",
             "Agree",
             "Really agree"
           )))  %>% 
  # outgroup-freq
  mutate(`outgroup_freq` = as_factor(`outgroup_freq`)) %>% 
  mutate(`outgroup_freq` = str_trim(`outgroup_freq`)) %>% 
  mutate(`outgroup_freq` = fct_relevel(`outgroup_freq`, c("Never",
                "Rarely",
                "Sometimes",
                "Often",
                "Very often")))

```

```{r recoding}
youtube <- youtube %>% 
  mutate(
    across(c(`homophily_appear_1`, `homophily_appear_2`, `homophily_appear_3`, `homophily_appear_4`, `homophily_appear_5`, `homophily_behave_1`, `homophily_behave_2`, `homophily_behave_3`, `homophily_behave_4`, `homophily_behave_6`, parasocial_1, parasocial_2, parasocial_3, parasocial_4, parasocial_5),
           ~ recode (.,
             "Really disagree" = 1,
             "Disagree" = 2,
             "I don't know" = 3,
             "Agree" = 4,
             "Really agree" = 5
           ))) %>% 
  mutate(
    across(c(malleable_1, malleable_2, malleable_3, malleable_4, regularities_1, regularities_2, regularities_3, regularities_4, regularities_5, regularities_6, regularities_7),
           ~ recode(.,
             "Really disagree" = 1,
             "Disagree" = 2,
             "Neither agree nor disagree" = 3,
             "Agree" = 4,
             "Really agree" = 5
           ))) %>%  
  select(-c(homophily_behave_5))
```

```{r stringr}
# Cleaning using stringr
youtube <- youtube %>% 
  # only keep last character in friend choice task
  mutate(friend = str_sub(friend, start = -1, end = -1)) %>% 
  # trim whitespace from free response
  mutate(favorite = str_squish(favorite))
```

```{r age}
# calculating child age
date_today <- Sys.Date()  
youtube <- youtube %>% 
  mutate(bday = as.Date(bday, format = "%m/%d/%Y")) %>% 
  mutate(age = age_calc(
    bday,
    date_today,
    units = "years"
  ))
```

```{r}
# Composite scores
# Racial attitudes score -- total possible score = 20
youtube <- youtube %>% 
  mutate(malleable_score = rowSums(across(malleable_1:malleable_4))) %>% 
  mutate(malleable_score = malleable_score/20)

# Parasocial relationship scores (each block separately, then aggregate)
youtube <- youtube %>% 
  # homophily-appear -- total possible score = 20
  mutate(h_appear_score = rowSums(across(`homophily-appear_1`:`homophily-appear_5`))) %>% 
  # homophily-behave -- total possible score = 20
  mutate(h_behave_score = rowSums(across(`homophily-behave_1`:`homophily-behave_6`))) %>% 
  # parasocial -- total possible score = 20
  mutate(parasocial_score = rowSums(across(parasocial_1:parasocial_5))) %>% 
  #Composite scores
  mutate(composite = rowSums(across(h_appear_score:parasocial_score))) %>% 
  # Proportion scores
  mutate(h_appear_score = h_appear_score/20) %>%
  mutate(h_behave_score = h_behave_score/20) %>%
  mutate(parasocial_score = parasocial_score/20) %>%
  mutate(composite = composite/60)

# Racial regularities score (behavior) -- total possible score = 35
youtube <- youtube %>% 
  # Reverse coded items
  mutate(across(c(behavior_3, behavior_5, behavior_7), ~ 6 - .)) %>% 
  # Score
  mutate(regularity_score = rowSums(across(behavior_1:behavior_7))) %>% 
  mutate(regularity_score = regularity_score/35)
```

```{r}
write_csv(youtube, "youtube.csv")
```

### 2025-03-08 manuscript.qmd
updated references
updated final qmd draft

@@
 library(broom)
+library(kableExtra)
+library(psych)
 library(tidyverse)
@@
 
+# read in data
+youtube <- read_csv("data/youtube.csv", col_names = TRUE)
+
 ```
-
-## Introduction
 
@@
 
-## Methods {#sec-methods}
+# Methods {#sec-methods}
 
 ### Participants and Procedures {#sec-participants-and-procedures}
-This study will include children between the ages of 8 and 13.
-Though children may express negative racial attitudes prior to this point in development, during early adolescence, children develop the ability to recognize and reflect on the racial patterns and dynamics present in their environments (Hughes & Watford, 2022).
-As such, this age range should allow me to observe how the observation racial regularities present on YouTube may affect children’s stereotyping and prejudicial attitudes, and how such a phenomenon develops.
-Participants will be recruited through Qualtrics Panels, which will allow me to obtain a representative sample of parents and children; other studies have used Qualtrics Panels with similar methods and populations (Byrd & Ahn, 2020).
+This study includes dyads of parents and children between the ages of 8 and 13 [^1].
+Though children may express negative racial attitudes prior to this point in development, during early adolescence, children develop the ability to recognize and reflect on the racial patterns and dynamics present in their environments [@hugheswatford_2022_racial].
+As such, this age range allows me to observe how the observation racial regularities present on YouTube may affect children’s stereotyping and prejudicial attitudes, and how such a phenomenon develops.
+Participants were recruited through Qualtrics Panels, allowing me to obtain a representative sample of parents and children; other studies have used Qualtrics Panels with similar methods and populations [@byrdahn_2020_profiles].
 
-Data will be collected during February and March of 2025 from families recruited via Qualtrics Panels.
-Participating families will receive two Qualtrics surveys to be completed asynchronously, and they will receive compensation (around $10-$15; the final amount will be determined by Qualtrics Panels) after both surveys have been completed.
-First, parents will complete a demographics and YouTube usage survey, in which they will answer questions related to parent and child demographics (child age, race/ethnicity, parent income and level of education, etc), as well as questions regarding their child’s YouTube usage (for instance, time spent on YouTube, as reported by their child’s device screen time).
-Then, children will complete their own survey.
+[^1]: Pilot data has demonstrated that Qualtrics Panels has not, thus far, been as stringent in participant age verification.
+As such, data used presently is from a broader age range than will be included in the final sample, after stricter age validation has been included.
+
+Pilot data has been collected in March of 2025 from families recruited via Qualtrics Panels (*N* = `r length(transaction_id)`).
+Participating families receive two Qualtrics surveys to be completed asynchronously, and receive compensation (as determined by Qualtrics Panels) after both surveys have been completed.
+First, parents complete a demographics and YouTube usage survey, then children complete their own survey.
 
 ### Measures {#sec-measures}
-First, they will answer questions related to their YouTube usage (perceptions of time spent).
+
+In the parent survey, participants answer questions related to parent and child demographics (child age, race/ethnicity, parent income and level of education, etc), as well as questions regarding their child’s YouTube usage (for instance, time spent on YouTube, as reported by their child’s device screen time).
+
+In the child survey, children answer questions related to their YouTube usage, such as time spent on YouTube and their favorite genre. 
 Next, they will either answer more questions pertaining to YouTube content, or their general racial attitudes; either block of questions will appear randomly, so as to reduce the influence of question order.
@@
 
-## Results {#sec-results}
+```{r}
+#| label: report-reliability-function
+#| echo: false
+#| message: false
+#| warning: false
+
+alpha(youtube %>% select(malleable_1:malleable_4))
+alpha(youtube %>% select(homophily_appear_1:homophily_appear_5))
+alpha(youtube %>% select(homophily_behave_1:homophily_behave_6))
+alpha(youtube %>% select(parasocial_1:parasocial_5))
+alpha(youtube %>% select(regularities_1:regularities_5))
+
+return_alpha <- function(data, cols) {
+  # select data 
+  selected_data <- data %>% select({{ cols }})
+  # compute alpha
+  alpha_result <- psych::alpha(selected_data, check.keys = TRUE)
+  # Extract and return the raw alpha value
+  return(alpha_result$total$raw_alpha)
+}
+
+reliability <- 
+  return_alpha(malleable_1:malleable_4) 
+```
+
+```{r}
+#| label: tbl-reliability
+#| tbl-cap: "Reliability of each scale used"
+#| echo: false
+#| message: false
+#| warning: false
+
+# Generate kable table
+kable(reliability, format = "html", caption = "Function Outputs in One Column") %>%
+  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))
+
+```
+
+# Results {#sec-results}
 
@@
 # BASED ON APAQUARTO DEMO - WILL CHANGE FOR FINAL; WANTED TO TEST RENDERING
-
-# read in data
-youtube <- read_csv("data/youtube.csv", col_names = TRUE)
 
@@
   return(report)    
-
 }
@@
 ```
+# Discussion
 
+\clearpage
 # References
+:::{refs}
+:::

### 2025-03-10 data/preparation_2.Rmd
updated data prep

@@
 ---
+
+MOVE TO R SCRIPT!
 
@@
 ```
+```{r}
+youtube <- youtube %>% 
+  mutate(
+    daily = ifelse(
+      days == "Every day",
+      "Every Day",
+      "Not Every Day"
+    )
+  ) %>% 
+  mutate(Ptime = as.numeric(Ptime))
+```
+
+```{r}
+youtube <- youtube %>% 
+  mutate(
+    race = ifelse(
+      race_ethnicity == "White",
+      "White",
+      "POC"
+    )
+  )
+```
 
@@
   mutate(
-    across(c(malleable_1, malleable_2, malleable_3, malleable_4, regularities_1, regularities_2, regularities_3, regularities_4, regularities_5, regularities_6, regularities_7),
+    across(c(malleable_1, malleable_2, malleable_3, malleable_4),
+           ~ recode(.,
+             "Really disagree" = 1,
+             "Disagree" = 2,
+             "Neither agree nor disagree" = 3,
+             "Agree" = 4,
+             "Really agree" = 5
+           ))) %>%  
+  mutate(
+    across(c(regularities_1, regularities_2, regularities_3, regularities_4, regularities_5, regularities_6, regularities_7),
            ~ recode(.,
@@
 
-```{r age}
-# calculating child age
+```{r birthdays}
 date_today <- Sys.Date()
+
+birthday <- function(df, column_name, date_today) {
+  df <- df %>%
+    mutate(
+      # Convert valid date strings to Date format
+      bday_date = if_else(
+        grepl("^\\d{2}/\\d{2}/\\d{4}$", .[[column_name]]), 
+        as.Date(.[[column_name]], format = "%m/%d/%Y"), 
+        NA_Date_
+      ),
+
+      # Extract last 4 characters for non-date values
+      bday_year = if_else(
+        is.na(bday_date), 
+        as.numeric(substr(.[[column_name]], nchar(.[[column_name]]) - 3, nchar(.[[column_name]]))), 
+        NA_real_
+      ),
+
+      # Calculate age based on actual date or extracted year
+      age = if_else(
+        !is.na(bday_date), 
+        as.numeric(difftime(date_today, bday_date, units = "days")) / 365.25, 
+        2025 - bday_year
+      )
+    ) %>%
+    select(-bday_date, -bday_year)  # Remove intermediate columns
+
+  return(df)
+}
+
+youtube <- birthday(youtube, "bday", date_today)
+
 youtube <- youtube %>% 
-  mutate(bday = as.Date(bday, format = "%m/%d/%Y")) %>% 
-  mutate(age = age_calc(
-    bday,
-    date_today,
-    units = "years"
-  ))
+  mutate(
+    in_range = case_when(
+      age < 14 ~ TRUE,
+      age >= 14 ~ FALSE
+    )
+  )
 ```
@@
   # homophily-appear -- total possible score = 20
-  mutate(h_appear_score = rowSums(across(`homophily-appear_1`:`homophily-appear_5`))) %>% 
+  mutate(h_appear_score = rowSums(across(homophily_appear_1:homophily_appear_5))) %>% 
   # homophily-behave -- total possible score = 20
-  mutate(h_behave_score = rowSums(across(`homophily-behave_1`:`homophily-behave_6`))) %>% 
+  mutate(h_behave_score = rowSums(across(homophily_behave_1:homophily_behave_6))) %>% 
   # parasocial -- total possible score = 20
@@
   # Reverse coded items
-  mutate(across(c(behavior_3, behavior_5, behavior_7), ~ 6 - .)) %>% 
+  mutate(across(c(regularities_3, regularities_5, regularities_7), ~ 6 - .)) %>% 
   # Score
-  mutate(regularity_score = rowSums(across(behavior_1:behavior_7))) %>% 
+  mutate(regularity_score = rowSums(across(regularities_1:regularities_7))) %>% 
   mutate(regularity_score = regularity_score/35)

### 2025-03-10 manuscript.qmd
updated manuscript draft

@@
 numbered-lines: false
-bibliography: [r-references.bib, bibliography.bib]
+bibliography: [r-references.bib, MA_THESIS.bib]
 link-citations: true
@@
 library(kableExtra)
+library(flextable)
 library(psych)
@@
 youtube <- read_csv("data/youtube.csv", col_names = TRUE)
+
+```
+
+```{r}
+#| label: my-theme
+#| echo: false
+#| message: false
+#| warning: false
+
+my_theme <- function(){
+  theme(
+    # Plot background color 
+    plot.background = element_rect(fill = NA),
+    # Adding border 
+    panel.border = element_rect(color = "black", fill = NA, linewidth = 0.5),
+    # Panel background
+    panel.background = element_rect(fill = NA),
+    # Plot labels
+    plot.title = element_text(color = "black", family = "serif", face = "bold"),
+    plot.subtitle = element_text(color = "black", family = "serif"),
+    plot.caption = element_text(color = "black", family = "serif", face = "italic"),
+    # Customizing grid lines 
+    panel.grid.major.y = element_line(color = "lightgrey", linetype = 1, linewidth = 0.5),
+    panel.grid.minor.y = element_blank(),
+    panel.grid.major.x = element_line(color = "lightgrey", linetype = 1, linewidth = 0.5),
+    panel.grid.minor.x = element_blank(),
+    # Customizing facets
+    strip.background = element_rect(color = "black", fill = NA),
+    strip.text = element_text(color = "black", hjust = 0.5, family = "serif"),
+    # Customizing axes
+    axis.text.y = element_text(color = "black", family = "serif", face = "bold.italic"),
+    axis.text.x = element_text(color = "black", family = "serif", face = "bold.italic"),
+    axis.title = element_text(color = "black", family = "serif", face = "bold"),
+    axis.ticks = element_line(color = "black"),
+    # Customizing legend
+    legend.title = element_text(color = "black", family = "serif", face = "italic"), 
+    legend.text = element_text(color = "black", family = "serif")
+  )
+}
 
@@
 ### Participants and Procedures {#sec-participants-and-procedures}
+
 This study includes dyads of parents and children between the ages of 8 and 13 [^1].
@@
 
-Pilot data has been collected in March of 2025 from families recruited via Qualtrics Panels (*N* = `r length(transaction_id)`).
+Pilot data has been collected in March of 2025 from families recruited via Qualtrics Panels (*N* = `r length(youtube$transaction_id)`).
 Participating families receive two Qualtrics surveys to be completed asynchronously, and receive compensation (as determined by Qualtrics Panels) after both surveys have been completed.
@@
 
+The particular measures used in the child survey are as follows:
+
+1. Beliefs about groups (adapted from @halperinetal_2012_promoting)
+2. Perceived homophily in behavior and appearance (adapted from @mccroskeyetal_1975_development)
+3. Parasocial interaction with a YouTuber (adapted from @sungetal_2023_shes)
+4. Racial regularities (created based on @rollinsetal_2022_who)
+5. Friend choice (adapted from @amemiyabian_2024_why)
+All measures used in adult studies have been specifically adapted for child readability.
+
 ```{r}
@@
 
-alpha(youtube %>% select(malleable_1:malleable_4))
-alpha(youtube %>% select(homophily_appear_1:homophily_appear_5))
-alpha(youtube %>% select(homophily_behave_1:homophily_behave_6))
-alpha(youtube %>% select(parasocial_1:parasocial_5))
-alpha(youtube %>% select(regularities_1:regularities_5))
-
 return_alpha <- function(data, cols) {
   # select data 
-  selected_data <- data %>% select({{ cols }})
+  selected_data <- data %>% select(all_of(cols))
   # compute alpha
@@
 }
+```
 
-reliability <- 
-  return_alpha(malleable_1:malleable_4) 
+```{r}
+#| label: reliability-df
+#| echo: false
+#| message: false
+#| warning: false
+
+measures <-
+  list(
+  "Group Malleability" = c("malleable_1", "malleable_2", "malleable_3", "malleable_4"),
+  "Homophily (Appearance)" = c("homophily_appear_1", "homophily_appear_2", "homophily_appear_3", "homophily_appear_4", "homophily_appear_5"),
+  "Homophily (Appearance)" = c("homophily_behave_1", "homophily_behave_2", "homophily_behave_3", "homophily_behave_4", "homophily_behave_6"),
+  "Parasociality" = c("parasocial_1", "parasocial_2", "parasocial_3", "parasocial_4", "parasocial_5"),
+  "Racial Regularities" = c("regularities_1", "regularities_2", "regularities_3", "regularities_4", "regularities_5")
+)
+
+reliability <- data.frame(
+  Measure = names(measures),
+  Alpha = sapply(measures, function(cols) return_alpha(youtube, cols))
+)
+
+reliability <- reliability %>%
+  mutate(Alpha = round(Alpha, digits = 2)) %>% 
+  mutate(
+    Evaluation = case_when(
+      Alpha >= 0.95 ~ "Excellent",
+      Alpha >= 0.9 ~ "Great",
+      Alpha >= 0.8 ~ "Good",
+      Alpha >= 0.7 ~ "Acceptable",
+      Alpha >= 0.6 ~ "Questionable",
+      Alpha < 0.6 ~ "Poor"
+    )
+  )
 ```
@@
 #| label: tbl-reliability
-#| tbl-cap: "Reliability of each scale used"
+#| tbl-cap: "Questionnaire Reliability"
 #| echo: false
@@
 
-# Generate kable table
-kable(reliability, format = "html", caption = "Function Outputs in One Column") %>%
-  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"))
+# Generate table
+kable(reliability, 
+      align = c("c", "c", "c"),
+      caption = "Reliability (assessed through Cronbach's Alpha) of questionnaires used, within sample") %>% 
+  kable_styling(position = "center", latex_options = c("striped"))
 
@@
 
+@tbl-reliability reports the reliability of all questionnaires used, within the present sample.
+
 # Results {#sec-results}
+
+Looking first to the distributions of time spent on YouTube among  participants, just as many children use YouTube every day as (*N* = `r sum(youtube$daily == 'Every Day')`) as those who do not (*N* = `r sum(youtube$daily == 'Not Every Day')`).
+And, as shown in @fig-time-distribution, children who use YouTube every day appear to use YouTube for more time on an average day than children who do not.
+On average, children spend about `r round(mean(youtube$Ptime), digits = 0)` minutes, or `r round(mean(youtube$Ptime)/60, digits = 0)` hour, on YouTube on an average day.
+
+```{r}
+#| label: fig-time-distribution
+#| fig-cap: "Distribution of watch time for kids"
+#| fig-align: "center"
+#| echo: false
+#| message: false
+#| warning: false
+
+# Set figure output settings - renders really small
+
+ggplot(subset(youtube, !is.na(Ctime)), aes(x = Ctime)) + 
+  geom_bar(color = "black", fill = "grey") +
+  facet_grid(~ daily) +
+  scale_x_discrete(labels = c("About 15 minutes a day" = "~ 15 min", "About 30 minutes a day" = "~ 30 min", "About 45 minutes a day" = "~ 45 min", "About 1 hour a day" = "~ 1 hr", "About 1 and 1/2 hours a day" = "~ 1.5 hr", "More than 2 hours a day" = "> 2 hr")) +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  ) +
+  labs(x = "Time Spent on YouTube",
+       y = "Number of Participants",
+       title = "Time Spent on YouTube on an Average Day",
+       subtitle = "Comparing children who use YouTube every day and children who do not") +
+  my_theme()
+
+```
+
+To what extent is time spent on YouTube predictive of how often children observe racial regularities?
+
+```{r}
+summary(aov(regularity_score ~ Ctime, data = youtube))
+summary(aov(regularity_score ~ outgroup_freq, data = youtube))
+```
+
+```{r}
+summary(aov(malleable_score ~ Ctime, data = youtube))
+summary(aov(malleable_score ~ outgroup_freq, data = youtube))
+```
+
+To what extent is time spent on YouTube predictive
 
@@
 
+summary(lm(malleable_score ~ regularity_score, data = youtube))
+
+t.test(malleable_score ~ race, data = youtube)
+t.test(regularity_score ~ race, data = youtube)
+
+t.test(malleable_score ~ daily, data = youtube)
+t.test(regularity_score ~ daily, data = youtube)
 ```
@@
 ```{r}
-#| label: regression-plot
+#| label: fig-regression-plot
 #| fig-cap: "Simple Correlation Between Time Spent on YouTube and Racial Attitudes score"
@@
 
-model_plot <- ggplot(youtube) +
-  aes(x = Ptime, y = malleable_score) +
-  geom_point() +
+ggplot(youtube) +
+  aes(x = regularity_score, y = malleable_score) +
+  geom_point(aes(color = daily)) +
   stat_smooth(method = "lm") +
-  scale_y_continuous(name = "Racial Attitudes Score") +
-  scale_x_continuous(name = "Time spent on YouTube")
-model_plot
+  facet_wrap(~ race) +
+  scale_y_continuous(name = "Malleability Score") +
+  scale_x_continuous(name = "Regularities Score") +
+  my_theme()
 

### 2025-03-11 data/preparation.R
Converted data prep to r script

@@ -1,31 +1,10 @@
----
-title: "preparation"
-author: "Reilly Amera"
-date: "2025-03-07"
-output: html_document
----
-
-MOVE TO R SCRIPT! 
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
-
-```{r packages}
-# Packages
 library(tidyverse)
-library(eeptools)
-```
 
-
-```{r read-in}
 # Read in data
-child <- read_csv("child.csv", col_names = TRUE)
-parent <- read_csv("parent.csv", col_names = TRUE)
-```
+child <- read_csv("data/child.csv", col_names = TRUE)
+parent <- read_csv("data/parent.csv", col_names = TRUE)
 
-```{r cleaning}
-# Data Cleaning
+########### Data Cleaning ###########
 
 # Remove rows that do not contain survey data
 parent <- parent[-c(1, 2),]
@@ -45,7 +24,9 @@ parent <- parent %>%
            ifelse(is.na(Q_RelevantIDDuplicate), FALSE, TRUE)) %>% 
   filter(Q_RelevantIDDuplicate != TRUE) %>% 
   # filter attn checks
-  filter(yt_opinions_4 == "A lot")
+  filter(yt_opinions_4 == "A lot") %>% 
+  # Ensure that time is numeric
+  mutate(Ptime = as.numeric(Ptime))
 
 # Child cleaning
 child <- child %>% 
@@ -62,153 +43,168 @@ parent <- parent %>%
 child <- child %>% 
   select(-c(StartDate:UserLanguage, opp, Q_BallotBoxStuffing:tg))
 
-```
-
-```{r merge}
+# Merge data frames
 youtube <- inner_join(parent, child, by = join_by(transaction_id))
-```
 
-```{r yt-factors}
-# CATEGORICAL: Dealing with Likert scales
+# Additional cleaning - favorite YouTuber
+youtube <- youtube %>% 
+  mutate(favorite = case_when(
+    favorite == "Mr beast" ~ "MrBeast",
+    favorite == "mr best" ~ "MrBeast",
+    favorite == "mr beast" ~ "MrBeast",
+    favorite == "Me beast" ~ "MrBeast",
+    is.na(favorite) ~ "None",
+    TRUE ~ favorite
+  )) %>% 
+  mutate(youtuber = ifelse(
+    favorite == "MrBeast",
+    "MrBeast",
+    "Not MrBeast"
+  ))
 
[…]

### 2025-03-12 manuscript.qmd
updated qmd

@@
     department: MA Program in the Social Sciences
+    address: "1155 E 60th St."
+    city: Chicago
+    region: IL
+    country: USA
+    postal-code: 60637
+abstract: "One way in which children learn about group dynamics within their racial world is from patterns in their daily environments.
+The current study seeks to understand the degree to which YouTube, a popular form of social media, exposes children to negatively valenced racial patterns, and potentially affects their beliefs.
+Dyads of parents and 8-13 year-old children (N = 18) describe daily YouTube usage, and the effects of children's YouTube usage are assessed.
+In the present sample, there is no relationship between children's YouTube usage, racial patterns they may observe, and negative racial beliefs."
 floatsintext: true
 numbered-lines: false
-bibliography: [r-references.bib, MA_THESIS.bib]
+bibliography: [r-references.bib, bibliography.bib]
 link-citations: true
@@
     list-of-tables: true
-    fig-width: 2
-    fig-height: 2
-    out-width: 40%
 editor: visual
@@
 
+# Necessary libraries
 library(svglite)
@@
 library(broom)
+#install.packages(kableExtra)
 library(kableExtra)
@@
 library(tidyverse)
+
+# Setting global options
+knitr::opts_chunk$set(
+  echo = FALSE,
+  message = FALSE,
+  warning = FALSE)
 
@@
 #| label: my-theme
-#| echo: false
-#| message: false
-#| warning: false
 
@@
 
-### Literature Review {#sec-lit-review}
+## Literature Review {#sec-lit-review}
 
@@
 
-### Present Study {#sec-present-study}
+## Present Study {#sec-present-study}
 
@@
 
-### Participants and Procedures {#sec-participants-and-procedures}
+## Participants and Procedures {#sec-participants-and-procedures}
 
@@
 
-### Measures {#sec-measures}
+## Measures {#sec-measures}
 
@@
 5. Friend choice (adapted from @amemiyabian_2024_why)
-All measures used in adult studies have been specifically adapted for child readability.
+
+All measures used in adult studies have been specifically adapted for child readability. @tbl-reliability reports the reliability of all questionnaires used, within the present sample.
 
@@
 #| label: report-reliability-function
-#| echo: false
-#| message: false
-#| warning: false
 
+# Function which returns Cronbach's alpha
 return_alpha <- function(data, cols) {
@@
 ```{r}
-#| label: reliability-df
-#| echo: false
-#| message: false
-#| warning: false
+#| label: reliability-dataframe
 
+# Creating a list of all measures, grouped by questionnaire
 measures <-
@@
 
+# Creating data frame with measures and corresponding alpha
 reliability <- data.frame(
@@
 
+# Adding column with evaluations of alpha
 reliability <- reliability %>%
@@
 #| label: tbl-reliability
-#| tbl-cap: "Questionnaire Reliability"
-#| echo: false
-#| message: false
-#| warning: false
+#| tbl-cap: "Reliability of Questionnaires"
 
@@
       align = c("c", "c", "c"),
+      # Setting caption here
       caption = "Reliability (assessed through Cronbach's Alpha) of questionnaires used, within sample") %>% 
@@
 
-@tbl-reliability reports the reliability of all questionnaires used, within the present sample.
+Beliefs about groups, particularly in terms of group malleability, were chosen as the primary outcome measure to assess racial attitudes.
+Such questions, adapted from @halperinetal_2012_promoting, address whether children have fixed or malleable views regarding outgroups (e.g.
+when prompted to think about groups with different skin colors than their own, children are asked the extent to which they agree with the statement, "These groups of people can't really change the way they act").
+Higher scores in this domain demonstrate more fixed evaluations of outgroup members, suggesting an underlying racial essentialism, or a belief in the intrinsic nature of racial difference [@waxman_2021_racial].
+
+Composite scores have been created for each measure. All analyses have been completed in RStudio [@R-base], primarily within the tidyverse and psych packages (@R-tidyverse; @R-psych).
 
@@
 And, as shown in @fig-time-distribution, children who use YouTube every day appear to use YouTube for more time on an average day than children who do not.
-On average, children spend about `r round(mean(youtube$Ptime), digits = 0)` minutes, or `r round(mean(youtube$Ptime)/60, digits = 0)` hour, on YouTube on an average day.
+On average, parents report that children spend about `r round(mean(youtube$Ptime), digits = 0)` minutes, or `r round(mean(youtube$Ptime)/60, digits = 0)` hour, on YouTube on an average day.
+Some children, as parents report, watch as much as `r round(max(youtube$Ptime)/60, digits = 0)` hours of YouTube, while others watch only `r round(min(youtube$Ptime)/60, digits = 0)`.
+Children's self-report YouTube usage reflects a similar pattern, as shown in @tbl-frequency: the majority of participants report watching YouTube for 30 minutes to 1 hour each day.
 
@@
 #| label: fig-time-distribution
-#| fig-cap: "Distribution of watch time for kids"
+#| fig-cap: "Distribution of participants' YouTube watch time"
 #| fig-align: "center"
-#| echo: false
-#| message: false
-#| warning: false
+#| fig-width: 6
+#| fig-height: 4
 
@@
   ) +
-  labs(x = "Time Spent on YouTube",
+  labs(x = "Time Spent on YouTube (Self-Reported)",
        y = "Number of Participants",
@@
 
-To what extent is time spent on YouTube predictive of how often children observe racial regularities?
+```{r}
+#| label: generate-frequency-table
 
-```{r}
-summary(aov(regularity_score ~ Ctime, data = youtube))
-summary(aov(regularity_score ~ outgroup_freq, data = youtube))
+frequency <- round(addmargins(prop.table(table(youtube$Ctime, youtube$daily))), 2)
 ```
@@
 ```{r}
-summary(aov(malleable_score ~ Ctime, data = youtube))
-summary(aov(malleable_score ~ outgroup_freq, data = youtube))
+#| label: tbl-frequency
+#| tbl-cap: "YouTube Screen Time Frequency Table"
+
+kable(frequency, 
+      align = c("c", "c", "c"),
+      # Setting caption here
+      caption = "Proportions of watch times in children who watch YouTube every day vs those who do not") %>% 
+  kable_styling(position = "center", latex_options = c("striped"))
 ```
 
-To what extent is time spent on YouTube predictive
+```{r}
+#| label: anova-outputs
+
+# ANOVA: racial regularities score predicted by time spent on YT (categorical self-report)
+aov_reg_ctime <- aov(regularity_score ~ Ctime, data = youtube)
+
+# ANOVA: racial regularities score predicted by perceptions of how often kids see outgroup (categorical)
+aov_reg_outfreq <- aov(regularity_score ~ outgroup_freq, data = youtube)
+
+# ANOVA: racial regularities score predicted by perceptions of how often kids see outgroup (categorical)
+aov_mall_outfreq <- aov(malleable_score ~ outgroup_freq, data = youtube)
+```
 
 ```{r}
-#| label: regression 
-#| echo: false
-#| message: false
-#| warning: false
+#| label: anova-report-function
 
-# BASED ON APAQUARTO DEMO - WILL CHANGE FOR FINAL; WANTED TO TEST RENDERING
+# based on apaquarto manuscript example and chat help
 
-# regression model
-model <- lm(malleable_score ~ Ptime, data = youtube)
+# Takes an aov model object as argument
+# Returns string of format "$F$(df1, df2) = F-value, $p$ = p-value"
 
-summary(lm(malleable_score ~ regularity_score, data = youtube))
+report_anova <- function(model) {
 
-t.test(malleable_score ~ race, data = youtube)
-t.test(regularity_score ~ race, data = youtube)
+  # make summary object
+  m_summary <- summary(model)[[1]]
+  # extract values
+  df1 <- m_summary$Df[1]
+  df2 <- m_summary$Df[2]
+  F_value <- m_summary$`F value`[1]
+  p_value <- m_summary$`Pr(>F)`[1]
+  # Create a string with the results
+  report <- paste0("$F$(", 
+                   df1,  ", ", 
+                   df2, ") = ", 
+                   round(F_value, 2), 
+                   ", $p$ = ", round(p_value, 3))
+  # Return report
+  return(report)    
+}
 
-t.test(malleable_score ~ daily, data = youtube)
-t.test(regularity_score ~ daily, data = youtube)
+```
+
+Preliminary one-way analysis of variance does not indicate that greater amounts of time spent on YouTube (self-report) is associated with a higher racial regularities score (`r report_anova(aov_reg_ctime)`).
+Similarly, thus far, one-way analysis of variance does not indicate that there is any association between ratings of frequency with which children encounter those of other racial groups and racial regularities scores, (`r report_anova(aov_reg_outfreq)`).
+Further, one-way analysis of variance does not indicate a significant relationship between the primary racial attitudes outcome measure, group malleability, and frequency of seeing racial outgroups on YouTube, (`r report_anova(aov_mall_outfreq)`).
+
+```{r}
+#| label: regression-models
+
+# Regressing malleability against time spent on YouTube (reported by parents)
+lm_mt <- lm(malleable_score ~ Ptime, data = youtube)
+
+# Regressing malleability against time spent on YouTube (reported by parents) and whether or not YouTube is used daily
+lm_mtd <- lm(malleable_score ~ Ptime + daily, data = youtube)
+
+# Regressing malleability against regularity
+lm_mr <- lm(malleable_score ~ regularity_score, data = youtube)
 ```
@@
 #| label: regression-report-functions
-#| echo: false
-#| message: false
-#| warning: false
 
-# BASED ON APAQUARTO DEMO - WILL CHANGE FOR FINAL; WANTED TO TEST RENDERING AND TRY INLINE REFERENCES
+# Taken from apaquarto demo
 
 # report_regression takes a lm model object as an argument
-# and returns a string of format:
-# "$F$(df, df.residual) = F-value, $p$ = p-value, $R^2$ = r-squared"
+# Returns string of format: "$F$(df, df.residual) = F-value, $p$ = p-value, $R^2$ = r-squared"
+
 report_regression <- function(model) {
@@
   m_glance <- glance(model)
-
   # Format the p-value
   p_value <- apa_p(m_glance$p.value, add_equals = TRUE)
-
   # Create a string with the results
@@
                    ") = ", round(m_glance$statistic, 2), 
-                   ", $p$ = ", p_value, ", $R^2$ = ", round(m_glance$r.squared,2))
-
+                   ", $p$ = ", p_value)
+  # Return report
   return(report)    
 }
+```
+
+Regressing malleability scores against parent reports of time spent on YouTube, no significant relationship is observed (`r report_regression(lm_mt)`).
+.
+This relationship remains unchanged and similarly insignificant when daily use is added as a predictor (`r report_regression(lm_mtd)`).
+Such relationships, as well as that of regularity score and YouTube usage, may be observed in @fig-malleable and @fig-regularity.
+Based on pilot sample alone, there is not enough data to conduct analyses with regard to the effect of YouTuber on racial attitudes, but the modal favorite YouTuber reported has thus far been `r mode(youtube$favorite)` (*N* = `r sum(youtube$favorite == 'MrBeast')`).
+Preliminary relationships between favorite YouTuber (this YouTuber in particular) as well as malleability and regularity scores may be found in @fig-malleable and @fig-regularity respectively.
+
+```{r}
+#| label: fig-malleable
+#| fig-cap: "Correlations Between Time Spent On YouTube and Group Malleability Beliefs"
+#| fig-scap: "Effects of time, daily use, and favorite YouTuber"
+#| fig-note: "MrBeast is the modal favorite YouTuber. No other YouTuber has been listed with enough frequency to report."
+#| fig-align: "center"
+#| fig-width: 5
+#| fig-height: 2
+
+ggplot(data = youtube %>% 
+             filter(Ptime > 10)) +
+  aes(x = Ptime, y = malleable_score) +
+  facet_grid(~ daily, scales = "free_x") +
+  stat_smooth(method = "lm", color = "#800000") +
+  geom_point(aes(shape = youtuber)) +
+  scale_shape_manual(values = c("Not MrBeast" = 16, "MrBeast" = 1)) +
+  labs(x = "Time Spent on YouTube (minutes)", y = "Malleability Score",
+       shape = "Favorite YouTuber") +
+  my_theme()
+```
+
+```{r}
+#| label: fig-regularity
+#| fig-cap: "Correlations Between Time Spent On YouTube and Racial Regularities"
+#| fig-scap: "Effects of time, daily use, and favorite YouTuber"
+#| fig-note: "MrBeast is the modal favorite YouTuber. No other YouTuber has been listed with enough frequency to report."
+#| fig-align: "center"
+#| fig-width: 5
+#| fig-height: 2
+
+ggplot(data = youtube %>% 
+             filter(Ptime > 10)) +
+  aes(x = Ptime, y = regularity_score) +
+  facet_grid(~ daily, scales = "free_x") +
+  stat_smooth(method = "lm", color = "#800000") +
+  geom_point(aes(shape = youtuber)) +
+  scale_shape_manual(values = c("Not MrBeast" = 16, "MrBeast" = 1)) +
+  labs(x = "Time Spent on YouTube (minutes)", y = "Regularity Score",
+       shape = "Favorite YouTuber") +
+  my_theme()
+```
+
+Just as there is not yet an observed relationship between time spent on YouTube and racial regularities, so too is there a lack of relationship between regularities scores and malleability scores in the present sample (`r report_regression(lm_mr)`).
+The preliminary relationship between racial regularity and malleability scores within the full sample may be found in @fig-full.
+Preliminary effects of daily YouTube usage and participant race may be found in @fig-faceted.
+
+```{r}
+#| label: fig-full
+#| fig-cap: "Correlation Between Racial Regularities Score and Malleability Score"
+#| fig-scap: "Full Sample"
+#| fig-note: "N = 18, only pilot data used."
+#| fig-align: "center"
+#| fig-width: 4
+#| fig-height: 3
+
+ggplot(youtube) +
+  aes(x = regularity_score, y = malleable_score) +
+  stat_smooth(method = "lm", color = "#800000", linewidth = 0.8, fill = "lightgrey") +
+  geom_point() +
+  labs(x = "Regularities Score", y = "Malleability Score",
+       title = "A") +
+  my_theme()
+```
+
+```{r}
+#| label: fig-faceted
+#| fig-cap: "Correlation Between Racial Regularities Score and Malleability Score"
+#| fig-scap: "Effects of daily use and participant race"
+#| fig-note: "Participant race coded as White/Non-White for pilot data only."
+#| fig-align: "center"
+#| fig-width: 4
+#| fig-height: 3
+
+ggplot(youtube) +
+  aes(x = regularity_score, y = malleable_score) +
+  stat_smooth(method = "lm", color = "black", linewidth = 0.8, fill = "lightgrey") +
+  geom_point(aes(color = race)) +
+  scale_color_manual(values = c("#155F83", "#C16622")) +
+  facet_wrap(~ daily) +
+  labs(x = "Regularities Score", y = "Malleability Score",
+       color = "Participant Race",
+       title = "B") +
+  theme(legend.position = "bottom") +
+   my_theme()
 
@@
 
-Below is a simple regression displaying the relationship between time spent on YouTube and a child's racial attitudes.
-Despite a visual upward trend, this relationship is not statistically significant: `r report_regression(model)`.
+# Discussion {#sec-discussion}
 
-```{r}
-#| label: fig-regression-plot
-#| fig-cap: "Simple Correlation Between Time Spent on YouTube and Racial Attitudes score"
-#| fig-scap: "Time v. Attitudes"
-#| fig-align: "center"
-#| fig-width: 6
-#| fig-height: 4
-#| echo: false
-#| message: false
-#| warning: false
-
-ggplot(youtube) +
-  aes(x = regularity_score, y = malleable_score) +
-  geom_point(aes(color = daily)) +
-  stat_smooth(method = "lm") +
-  facet_wrap(~ race) +
-  scale_y_continuous(name = "Malleability Score") +
-  scale_x_continuous(name = "Regularities Score") +
-  my_theme()
-
-```
-# Discussion
+The present study examines the relationship between children's YouTube usage and potential effects on racial attitudes.
+No significant effects of YouTube usage on group beliefs have been observed thus far; we thus fail to reject the null hypothesis that there is no difference in racial beliefs between children who spend a lot of time on YouTube and those who do not.
+Similarly, as there is no significant relationship between time spent on YouTube and children's observation of racial regularities, nor between racial regularities and group malleability beliefs, there is no evidence thus far to suggest that observation of racial regularities affects outgroup prejudices as a result of YouTube usage.
 

### 2025-03-12 data/preparation.R
finalized data preparation

@@ -243,5 +243,5 @@ youtube <- youtube %>%
   mutate(regularity_score = rowSums(across(regularities_1:regularities_7))) %>% 
   mutate(regularity_score = regularity_score/35)
 
-### 
+### Write out data set
 write_csv(youtube, "data/youtube.csv")

### 2025-03-12 manuscript.qmd
FINAL .QMD VERSION

@@
 # Necessary libraries
-library(svglite)
+#install.packages(papaja)
 library(papaja)
+#install.packages(kableExtra)
+library(kableExtra)
+#install.packages(psych)
+library(psych)
 library(knitr)
 library(broom)
-#install.packages(kableExtra)
-library(kableExtra)
-library(flextable)
-library(psych)
 library(tidyverse)
@@
 
-# Generate or overwrite r-reference files
-# papaja::r_refs(file = "r-references.bib")
+# Set seed
+set.seed(521)
 
@@
 
+# Custom theme
 my_theme <- function(){
@@
 
-In the parent survey, participants answer questions related to parent and child demographics (child age, race/ethnicity, parent income and level of education, etc), as well as questions regarding their child’s YouTube usage (for instance, time spent on YouTube, as reported by their child’s device screen time).
+In the parent survey, participants answer questions related to parent and child demographics (child age, race/ethnicity, parent income and level of education, etc.), as well as questions regarding their child’s YouTube usage (for instance, time spent on YouTube, as reported by their child’s device screen time).
 
@@
 
+# Created with ChatGPT help
 # Function which returns Cronbach's alpha
@@
 #| fig-cap: "Distribution of participants' YouTube watch time"
-#| fig-align: "center"
 #| fig-width: 6
 #| fig-height: 4
-
-# Set figure output settings - renders really small
 
@@
 
-# based on apaquarto manuscript example and chat help
+# based on apaquarto manuscript example and chatGPT help
 
@@
 # report_regression takes a lm model object as an argument
-# Returns string of format: "$F$(df, df.residual) = F-value, $p$ = p-value, $R^2$ = r-squared"
+# Returns string of format: "$F$(df, df.residual) = F-value, $p$ = p-value"
 
@@
                    ") = ", round(m_glance$statistic, 2), 
-                   ", $p$ = ", p_value)
+                   ", $p$ ", p_value)
   # Return report
@@
 #| fig-cap: "Correlations Between Time Spent On YouTube and Group Malleability Beliefs"
-#| fig-scap: "Effects of time, daily use, and favorite YouTuber"
-#| fig-note: "MrBeast is the modal favorite YouTuber. No other YouTuber has been listed with enough frequency to report."
-#| fig-align: "center"
 #| fig-width: 5
@@
 ggplot(data = youtube %>% 
+         # filtering outliers that are too low
              filter(Ptime > 10)) +
@@
   labs(x = "Time Spent on YouTube (minutes)", y = "Malleability Score",
-       shape = "Favorite YouTuber") +
+       shape = "Favorite YouTuber",
+       title = "Malleability and Time Spent on YouTube",
+       caption = "Note: MrBeast is the modal favorite YouTuber.") +
   my_theme()
@@
 #| fig-cap: "Correlations Between Time Spent On YouTube and Racial Regularities"
-#| fig-scap: "Effects of time, daily use, and favorite YouTuber"
-#| fig-note: "MrBeast is the modal favorite YouTuber. No other YouTuber has been listed with enough frequency to report."
-#| fig-align: "center"
 #| fig-width: 5
@@
   labs(x = "Time Spent on YouTube (minutes)", y = "Regularity Score",
-       shape = "Favorite YouTuber") +
+       shape = "Favorite YouTuber",
+       title = "Racial Regularities and Time Spent on YouTube",
+       caption = "Note: MrBeast is the modal favorite YouTuber.") +
   my_theme()
@@
 Just as there is not yet an observed relationship between time spent on YouTube and racial regularities, so too is there a lack of relationship between regularities scores and malleability scores in the present sample (`r report_regression(lm_mr)`).
-The preliminary relationship between racial regularity and malleability scores within the full sample may be found in @fig-full.
-Preliminary effects of daily YouTube usage and participant race may be found in @fig-faceted.
+The preliminary relationship between racial regularity and malleability scores within the full sample, as well as preliminary effects of daily YouTube usage and participant race may be found in @fig-reg-v-mall.
 
 ```{r}
-#| label: fig-full
+#| label: fig-reg-v-mall
 #| fig-cap: "Correlation Between Racial Regularities Score and Malleability Score"
-#| fig-scap: "Full Sample"
-#| fig-note: "N = 18, only pilot data used."
-#| fig-align: "center"
-#| fig-width: 4
-#| fig-height: 3
+#| fig-subcap: ["Full Sample", "Effects of daily use and participant race"]
+#| layout-ncol: 2
+#| fig-height: 6
 
+# Arrange plots (chatgpt rendering assistance)
+par(mfrow = c(1, 2))
+
+# Plot 1: Full sample
 ggplot(youtube) +
@@
   labs(x = "Regularities Score", y = "Malleability Score",
-       title = "A") +
+       title = "Malleability vs. Regularity Scores") +
+  theme(plot.title = element_text(size = 20), 
+            axis.text = element_text(size = 16),
+            axis.title = element_text(size = 18)) +
   my_theme()
-```
 
-```{r}
-#| label: fig-faceted
-#| fig-cap: "Correlation Between Racial Regularities Score and Malleability Score"
-#| fig-scap: "Effects of daily use and participant race"
-#| fig-note: "Participant race coded as White/Non-White for pilot data only."
-#| fig-align: "center"
-#| fig-width: 4
-#| fig-height: 3
-
+# Plot 2: Faceted plot
 ggplot(youtube) +
@@
        color = "Participant Race",
-       title = "B") +
-  theme(legend.position = "bottom") +
+       title = "Malleability vs. Regularity Scores",
+       caption = "Note: Participant race coded as White/Non-White for pilot data only.") +
+  theme(legend.position = "bottom",
+        plot.title = element_text(size = 20), 
+        axis.text = element_text(size = 16),
+        axis.title = element_text(size = 18), 
+        legend.title = element_text(size = 18),
+        legend.text = element_text(size = 16),
+        plot.caption = element_text(size = 14)) +
   my_theme()
-
 ```
@@
 The present study examines the relationship between children's YouTube usage and potential effects on racial attitudes.
-No significant effects of YouTube usage on group beliefs have been observed thus far; we thus fail to reject the null hypothesis that there is no difference in racial beliefs between children who spend a lot of time on YouTube and those who do not.
+No significant effects of YouTube usage on group beliefs have been observed thus far; within the present study, we thus fail to reject the null hypothesis that there is no difference in racial beliefs between children who spend a lot of time on YouTube and those who do not.
 Similarly, as there is no significant relationship between time spent on YouTube and children's observation of racial regularities, nor between racial regularities and group malleability beliefs, there is no evidence thus far to suggest that observation of racial regularities affects outgroup prejudices as a result of YouTube usage.
+
+Though no relationships have been observed thus far, the present sample is limited in size.
+There is still potential that relationships between YouTube usage, children's observations of racial regularities, and children's expression of group malleability beliefs may emerge in the full sample.
+Further, there is possibility that with the full sample, there is greater evidence for the effect of parasociality.
+Should the full sample yield such results, this would suggest that YouTube is indeed a site of racial socialization for children.
+As it is still currently unknown whether racial regularities are transmitted via social media platforms in a manner that leads to negative attitudes, and this study will be a first step toward understanding such an impact.
+Additionally, if in the full sample if there are significant differences in racial stereotyping and prejudice based on a favorite YouTuber, this would indicate YouTubers as potential points of intervention in a child’s development of racial attitudes and behaviors.
+
+Considering the dearth of research on how social media platforms affect children’s racial attitudes and behaviors, this study will provide insights into the extent to which various aspects of social media usage contribute to racial socialization.
+With the future, full sample, findings may still lead to novel discoveries and interventions in the development of negative racial attitudes and behavior.
 

### 2025-03-31 d2mr_manuscript.qmd
Updating document names to reflect full sample data

--- 2025-03-12 manuscript.qmd
@@
 If positive parasocial contact hypothesis effects may be observed when individuals form relationships with characters in other media, so too should these effects be observed when individuals have parasocial relationships with outgroup influencers [@banasetal_2020_metaanalysis].
-Thus, I pose my third hypothesis: the relationship between the amount of time that children spend on YouTube and their racial stereotyping and prejudice will be moderated by whether they have a parasocial relationship with a favorite YouTuber of a race other than their own.
+Thus, I pose my final hypothesis: the relationship between the amount of time that children spend on YouTube and their racial stereotyping and prejudice will be moderated by whether they have a parasocial relationship with a favorite YouTuber of a race other than their own.
 Specifically, if children have a favorite YouTuber of a race other than their own and they have a parasocial relationship with this YouTuber, they will display less racial stereotyping and prejudice.

### 2025-03-31 data/preparation.Rmd
Added informative comment
Updating document names to reflect full sample data

--- 2025-02-26 data/preparation.Rmd
@@
 author: "Reilly Amera"
-date: "2025-02-26"
+date: "2025-03-24"
 output: html_document
@@
 
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+```
+
 ```{r setup}
 library(tidyverse)
-```
 
-```{r read-in}
+# Read in data
 child <- read_csv("child.csv", col_names = TRUE)
@@
 ```{r cleaning}
-# removing unnecessary columns
-child <- child %>% 
-  select(-c(1:5, 8:18))
+# Remove rows that do not contain survey data
+parent <- parent[-c(1, 2),]
 child <- child[-c(1, 2),]
-
-parent <- parent %>% 
-  select(-c(1:6, 8:18))
-parent <- parent[-c(1, 2),]
-
-# replacing one NA (participant forgot ID)
-child$PID[is.na(child$PID)] <- 1
-
-# renaming 'finished' columns 
-child <- child %>% 
-  rename(Cfinished = Finished)
-
-parent <- parent %>% 
-  rename(Pfinished = Finished)
 ```
 
-```{r wrangling}
-# merging datasets
-youtube <- full_join(parent, child, by = "PID")
+```{r parent cleaning}
+# Parent cleaning
+parent <- parent %>% 
+  # self consent = agree
+  filter(Pconsent_self == "Agree") %>% 
+  # child consent = agree
+  filter(`Pconsent-child` == "Agree") %>% 
+  # remove duplicates
+  mutate(Q_RelevantIDDuplicate = 
+           # Logical operators
+           ifelse(is.na(Q_RelevantIDDuplicate), FALSE, TRUE)) %>% 
+  filter(Q_RelevantIDDuplicate != TRUE) %>% 
+  # filter attn checks
+  filter(yt_opinions_4 == "A lot") %>% 
+  # get rid of unnecessary columns
+  select(-c(StartDate:Q_RelevantIDLastStartDate))
+```
 
-# removing instances where either parents or children failed to finish
+```{r parent wrangling}
+# Parent reported child age
+parent <- parent %>% 
+  # Create one birthday column
+  unite(bday, `bday#1_1`, `bday#2_1`, sep = " ", remove = FALSE) %>% 
+  unite(bday, bday, `bday#3_1`, sep = ", ", remove = FALSE) %>% 
+  # Parse birthdays as dates
+  mutate(bday = mdy(bday)) %>% 
+  # Age column
+  mutate(P_age = time_length(interval(bday, Sys.Date()), "years") %>% floor())
+```
+
+```{r child cleaning}
+child <- child %>% 
+  # remove survey testing responses 
+  filter(!is.na(transaction_id)) %>% 
+  # consent = agree
+  filter(Cconsent == "YES") %>% 
+  # get rid of unnecessary columns
+  select(-c(StartDate:UserLanguage)) %>% 
+  # gc = 1 - embedded data; good/complete responses
+  filter(gc == 1)
+```
+
+```{r merge}
+# Merging data
+youtube <- inner_join(parent, child, by = join_by(transaction_id))
+```
+
+```{r age wrangling}
 youtube <- youtube %>% 
-  filter(Pfinished == Cfinished)
+  # Do child ages match parent ages?
+  mutate(age_match = ifelse(
+    P_age == age,
+    TRUE,
+    FALSE
+  ))
+
+# age discrepancies
+false_age <- youtube %>% 
+  select(age_match, bday, P_age, age, transaction_id) %>% 
+  filter(age_match == FALSE) %>% 
+  mutate(age = as.numeric(age)) %>% 
+  mutate(difference = abs(P_age - age)) %>% 
+  mutate(large_diff = ifelse(
+    difference > 1,
+    TRUE,
+    FALSE
+  )) %>% 
+  filter(large_diff == TRUE) %>% 
+  select(transaction_id)
+
+# write_csv(false_age, "transaction_ids.csv")
 ```
+
+```{r youtube wrangling}
+# Time Scores
+```
+
+```{r youtube composites}
+### Recoding factor variables as numeric variables to create aggregate scores
+youtube <- youtube %>% 
+  mutate(
+    across(c(`homophily_appear_1`, `homophily_appear_2`, `homophily_appear_3`, `homophily_appear_4`, `homophily_appear_5`, `homophily_behave_1`, `homophily_behave_2`, `homophily_behave_3`, `homophily_behave_4`, `homophily_behave_6`, parasocial_1, parasocial_2, parasocial_3, parasocial_4, parasocial_5),
+           ~ recode (.,
+                     "Really disagree" = 1,
+                     "Disagree" = 2,
+                     "I don't know" = 3,
+                     "Agree" = 4,
+                     "Really agree" = 5
+           ))) %>% 
+  mutate(
+    across(c(malleable_1, malleable_2, malleable_3, malleable_4),
+           ~ recode(.,
+                    "Really disagree" = 1,
+                    "Disagree" = 2,
+                    "Neither agree nor disagree" = 3,
+                    "Agree" = 4,
+                    "Really agree" = 5
+           ))) %>%  
+  mutate(
+    across(c(regularities_1, regularities_2, regularities_3, regularities_4, regularities_5, regularities_6, regularities_7),
+           ~ recode(.,
+                    "Really disagree" = 1,
+                    "Disagree" = 2,
+                    "Neither agree nor disagree" = 3,
+                    "Agree" = 4,
+                    "Really agree" = 5
+           ))) %>%  
+  select(-c(homophily_behave_5))
+
+### Composite scores
+# Racial attitudes score -- total possible score = 20
+youtube <- youtube %>% 
+  mutate(malleable_score = rowSums(across(malleable_1:malleable_4))) %>% 
+  mutate(malleable_score = malleable_score/20)
+
+# Parasocial relationship scores (each block separately, then aggregate)
+youtube <- youtube %>% 
+  # homophily-appear -- total possible score = 20
+  mutate(h_appear_score = rowSums(across(homophily_appear_1:homophily_appear_5))) %>% 
+  # homophily-behave -- total possible score = 20
+  mutate(h_behave_score = rowSums(across(homophily_behave_1:homophily_behave_6))) %>% 
+  # parasocial -- total possible score = 20
+  mutate(parasocial_score = rowSums(across(parasocial_1:parasocial_5))) %>% 
+  #Composite scores
+  mutate(composite = rowSums(across(h_appear_score:parasocial_score))) %>% 
+  # Proportion scores
+  mutate(h_appear_score = h_appear_score/20) %>%
+  mutate(h_behave_score = h_behave_score/20) %>%
+  mutate(parasocial_score = parasocial_score/20) %>%
+  mutate(composite = composite/60)
+
+# Racial regularities score (behavior) -- total possible score = 35
+youtube <- youtube %>% 
+  # Reverse coded items
+  mutate(across(c(regularities_3, regularities_5, regularities_7), ~ 6 - .)) %>% 
+  # Score
+  mutate(regularity_score = rowSums(across(regularities_1:regularities_7))) %>% 
+  mutate(regularity_score = regularity_score/35)
+```
+
+```{r}
+# H1: time spent on YouTube and children’s observation of racial regularities covary
+```
+
+```{r}
+# H2: if children spend more time on YouTube, they will display greater racial stereotyping and prejudice against outgroups
+```
+
+```{r}
+# H3: the relationship between children’s time spent on YouTube and their exhibited racial stereotyping and prejudice will be mediated by their observations of negative racial regularities
+```
+
+```{r}
+# H4: the relationship between the amount of time that children spend on YouTube and their racial stereotyping and prejudice will be moderated by whether they have a parasocial relationship with a favorite YouTuber of a race other than their own
+```

### 2025-03-31 pilot_data/preparation.R

@@ -1,8 +1,8 @@
 library(tidyverse)
 
 # Read in data
-child <- read_csv("data/child.csv", col_names = TRUE)
-parent <- read_csv("data/parent.csv", col_names = TRUE)
+child <- read_csv("pilot_data/child.csv", col_names = TRUE)
+parent <- read_csv("pilot_data/parent.csv", col_names = TRUE)
 
 ########### Data Cleaning ###########
 

### 2025-04-14 d2mr_manuscript.qmd
old manuscript (d2mr)

@@
 The current study seeks to understand the degree to which YouTube, a popular form of social media, exposes children to negatively valenced racial patterns, and potentially affects their beliefs.
-Dyads of parents and 8-13 year-old children (N = 18) describe daily YouTube usage, and the effects of children's YouTube usage are assessed.
+Dyads of parents and 8-13 year-old children (N = 200 dyads) describe daily YouTube usage, and the effects of children's YouTube usage are assessed.
 In the present sample, there is no relationship between children's YouTube usage, racial patterns they may observe, and negative racial beliefs."
@@
 #| layout-ncol: 2
-#| fig-height: 6
+#| dfig-height: 6
 

### 2025-04-14 data/preparation.Rmd
updated data cleaning, wrangling, and other thesis-prep

@@
 ```{r setup}
+library(psych)
+library(knitr)
+library(broom)
+library(papaja)
+library(mediation)
 library(tidyverse)
@@
 parent <- read_csv("parent.csv", col_names = TRUE)
+child_old <- read_csv("child_old.csv", col_names = TRUE)
+parent_old <- read_csv("parent_old.csv", col_names = TRUE)
+```
+
+```{r label}
+# Marking new data with "1"
+child$new_sample <- ifelse(child$transaction_id %in% child_old$transaction_id, 0, 1)
+parent$new_sample <- ifelse(parent$transaction_id %in% parent_old$transaction_id, 0, 1)
 ```
@@
 # age discrepancies
-false_age <- youtube %>% 
-  select(age_match, bday, P_age, age, transaction_id) %>% 
-  filter(age_match == FALSE) %>% 
+youtube <- youtube %>% 
+  # age as numeric
   mutate(age = as.numeric(age)) %>% 
+  # add column measuring difference in responses
   mutate(difference = abs(P_age - age)) %>% 
@@
     FALSE
-  )) %>% 
-  filter(large_diff == TRUE) %>% 
-  select(transaction_id)
+  ))
 
-# write_csv(false_age, "transaction_ids.csv")
+sum(youtube$large_diff)
+
+summary(youtube$age)
+
 ```
@@
 # Time Scores
+
+# Parent time report
+youtube <- youtube %>% 
+  mutate(Pdays = ifelse(Pdays == "None", 0, Pdays)) %>% 
+  mutate(Pdays = str_sub(Pdays, start = 1, end = 1)) %>%
+  mutate(Ptime = as.character(Ptime)) %>% 
+  mutate(Ptime = dplyr::recode(Ptime,
+                        "0 minutes" = 0,
+                        "15 minutes or less" = 1,
+                        "30 minutes or less" = 2,
+                        "45 minutes or less" = 3,
+                        "1 hour or less" = 4,
+                        "1.5 hours or less" = 5,
+                        "2 hours or less" = 6,
+                        "More than 2 hours" = 7,
+                        # Only 1 instance of other; participant listed 2 (presumably 2 hours)
+                        "Other" = 6
+                        )) %>% 
+  mutate(Pdays = as.numeric(Pdays)) %>%
+  mutate(Ptime = as.numeric(Ptime)) %>%
+  mutate(Ptime_score = Pdays * Ptime)
+
+# Survey logic was "If 1 AND 2 were selected, show next block" - about 9 responses
+# Just using parent data
+```
+
+```{r time binned}
+youtube <- youtube %>% 
+  mutate(Ptime_max = case_when(
+                        Ptime == "0" ~ 0,
+                        Ptime == "1" ~ 0.25,
+                        Ptime == "2" ~ 0.5,
+                        Ptime == "3" ~ 0.75,
+                        Ptime == "4" ~ 1,
+                        Ptime == "5" ~ 1.5,
+                        Ptime == "6" ~ 2,
+                        Ptime == "7" ~ 3,
+                        TRUE ~ NA_real_
+                        )) %>% 
+  mutate(Ptime_max = as.numeric(Ptime_max)) %>%
+  mutate(Ptime_max_score = Pdays * Ptime_max)
+```
+
+```{r time correlation}
+# Degree to which parent and child reports of time are correlated
+
+# Youtube correlation with all responses, parent replacing 10 -- 0.9319548
+# Correlating parent and child data for responses of 3-7 days -- 0.9168719
+x <- youtube %>%
+  mutate(days = str_sub(days, start = 1, end = 1)) %>%
+  filter(!(days %in% c(1, 2))) %>% 
+cor(youtube$Pdays, youtube$days, method = "pearson")
+
+# see correlation in Ctime - 0.732496
+test <- youtube %>%
+  filter(!(days %in% c(1, 2, "N"))) %>% 
+  mutate(Ctime = case_when(
+    Ctime == "0 minutes" ~  0,
+    Ctime == "15 minutes or less" ~ 1,
+    Ctime == "30 minutes or less" ~ 2,
+    Ctime == "45 minutes or less" ~ 3,
+    Ctime == "1 hour or less" ~ 4,
+    Ctime == "1.5 hours or less" ~ 5,
+    Ctime == "2 hours or less" ~ 6,
+    Ctime == "More than 2 hours" ~ 7,
+    TRUE ~ NA_real_)) %>% 
+  mutate(Ctime = as.numeric(Ctime)) %>% 
+  mutate(time_match = ifelse(Ctime == Ptime,
+                             1, 0)) %>% 
+  select(Ptime, Pdays, Ctime, days, time_match) %>%
+  mutate(diff = abs(Ptime - Ctime)) %>% 
+  mutate(large_diff = ifelse(diff > 2,
+    TRUE,
+    FALSE))
+sum(test$large_diff)
+cor(test$Ptime, test$Ctime, method = "pearson")
+# Use parent values as primary predictor; report correlation for responses
+
+# Consider how to report time scores in writing 
+summary(youtube$Ptime)
 ```
@@
     across(c(`homophily_appear_1`, `homophily_appear_2`, `homophily_appear_3`, `homophily_appear_4`, `homophily_appear_5`, `homophily_behave_1`, `homophily_behave_2`, `homophily_behave_3`, `homophily_behave_4`, `homophily_behave_6`, parasocial_1, parasocial_2, parasocial_3, parasocial_4, parasocial_5),
-           ~ recode (.,
+           ~ dplyr::recode (.,
                      "Really disagree" = 1,
@@
     across(c(malleable_1, malleable_2, malleable_3, malleable_4),
-           ~ recode(.,
+           ~ dplyr::recode(.,
                     "Really disagree" = 1,
@@
     across(c(regularities_1, regularities_2, regularities_3, regularities_4, regularities_5, regularities_6, regularities_7),
-           ~ recode(.,
+           ~ dplyr::recode(.,
                     "Really disagree" = 1,
@@
 youtube <- youtube %>% 
-  # homophily-appear -- total possible score = 20
+  # homophily-appear -- total possible score = 25
   mutate(h_appear_score = rowSums(across(homophily_appear_1:homophily_appear_5))) %>% 
-  # homophily-behave -- total possible score = 20
+  # homophily-behave -- total possible score = 25
   mutate(h_behave_score = rowSums(across(homophily_behave_1:homophily_behave_6))) %>% 
-  # parasocial -- total possible score = 20
+  # parasocial -- total possible score = 25
   mutate(parasocial_score = rowSums(across(parasocial_1:parasocial_5))) %>% 
@@
   # Proportion scores
-  mutate(h_appear_score = h_appear_score/20) %>%
-  mutate(h_behave_score = h_behave_score/20) %>%
-  mutate(parasocial_score = parasocial_score/20) %>%
-  mutate(composite = composite/60)
+  mutate(h_appear_score = h_appear_score/25) %>%
+  mutate(h_behave_score = h_behave_score/25) %>%
+  mutate(parasocial_score = parasocial_score/25) %>%
+  mutate(composite = composite/75)
 
@@
   mutate(regularity_score = regularity_score/35)
+
+# presenting raw data can contextualize the data - make sure to say that 1.0 is highly fixed, eg, and 0.5 is neutral
+```
+
+```{r friend cleaning}
+# Friend Choice cleaning
+
+# Splitting multiple races
+youtube <- youtube %>%
+  separate(race_ethnicity, into = c("race_1", "race_2", "race_3"), sep = ",\\s*")
+
+# Recoding kid race and gender based on method design
+youtube <- youtube %>% 
+  # Trim "kid"
+  mutate(friend = str_extract(friend, "\\d+")) %>%  
+  # Add gender
+  mutate(friend_gender = case_when(
+    friend %in% c(1, 3, 5, 7, 9)  ~ "Male",
+    friend %in% c(2, 4, 6, 8, 10) ~ "Female",
+    TRUE ~ as.character(friend)
+    )) %>% 
+  # Recode based on race
+  mutate(friend_race = case_when(
+    friend %in% c(1, 4)  ~ "Black or African American",
+    friend %in% c(2, 9)  ~ "White",
+    friend %in% c(3, 6)  ~ "Hispanic or Latino/a",
+    friend %in% c(5, 8)  ~ "South Asian",
+    friend %in% c(7, 10)  ~ "Asian",
+    TRUE ~ as.character(friend)
+    ))
+
+# Matches
+# Race match = 1, race does not match = 2, race not represented = 3
+youtube <- youtube %>% 
+  mutate(race_match = case_when(
+    race_1 %in% c("American Indian or Alaska Native", "Middle Eastern or North African", "Native Hawaiian or Other Pacific Islander", "Some Other Race", "Multiracial") ~ 2,
+    friend_race == race_1 ~ 1, 
+    friend_race != race_1 ~ 0,
+    TRUE ~ NA_real_
+  )) %>% 
+  mutate(race_match_binary = ifelse(race_match == 1, 1, 0)) %>% 
+  relocate(race_1, .after = friend_race) %>% 
+  # gender match
+  mutate(gender_match = ifelse(
+    friend_gender == gender,
+    1, 0
+  ))
+```
+
+```{r}
+write_csv(youtube, "youtube.csv")
+```
+
+```{r}
+# YouTuber cleaning
+
+favorite <- youtube %>% 
+  dplyr::select(favorite, transaction_id)
+
+write_csv(favorite, "favorite.csv")
+```
+
+```{r demographic descriptives }
+# Descriptive statistics - demographics
+
+# Age
+ggplot(data = youtube) +
+  aes(x = age) + 
+  geom_bar(color = "black", fill = "grey")
+
+# Race
+ggplot(data = youtube) +
+  aes(x = race_1) + 
+  geom_bar(color = "black", fill = "grey")
+
+# Gender
+ggplot(data = youtube) +
+  aes(x = gender) + 
+  geom_bar(color = "black", fill = "grey")
+```
+
+```{r time descriptives}
+# Descriptive statistics - time
+
+# Histogram of parent reported time spent on YouTube
+ggplot(data = youtube) +
+  aes(x = Pdays) + 
+  geom_bar(color = "black", fill = "grey")
+
+# Histogram of parent reported days per week spent on YouTube
+ggplot(data = youtube) +
+  aes(x = Ptime) + 
+  geom_bar(color = "black", fill = "grey")
+
+# Histogram of parent time score spent on YouTube
+ggplot(data = youtube) +
+  aes(x = Ptime_score) + 
+  geom_bar(color = "black", fill = "grey")
+
+# Histogram of parent time score spent on YouTube - minutes as opposed to scores
+ggplot(data = youtube) +
+  aes(x = Ptime_max_score) + 
+  geom_bar(color = "black", fill = "grey")
+
+ggplot(data = youtube) +
+  aes(x = Ptime_score) +
+  geom_boxplot()
+summary(youtube$Ptime_score)
+
+ggplot(data = youtube) +
+  aes(x = race_1) +
+  geom_bar()
+
+```
+
+```{r regularity descriptive}
+# Regularities
+ggplot(data = youtube) +
+  aes(x = regularity_score) + 
+  geom_bar(color = "black", fill = "grey")
+
+ggplot(data = youtube) +
+  aes(x = regularity_score) + 
+  geom_boxplot(color = "black", fill = "grey")
+
+summary(youtube$regularity_score)
+
+sd(youtube$regularity_score)
+# t.test
+
+# Negative outgroup prejudice overall 
+# run t test for just white kids alone?
+
+t.test(youtube$regularity_score, mu = 0.5)
+```
+
+```{r}
+# variance relative to t test
+individual_means <- rowMeans(youtube[, paste0("regularities_", 1:7)], na.rm = TRUE)
+
+# Center scores around the target mean
+centered <- individual_means - 2.572143
+
+# Variance
+variance <- mean(centered^2)
+
+# Standard deviation
+std_dev <- sqrt(variance)
+
+variance
+std_dev
+```
+
+```{r}
+# Alpha
+
+# Created with ChatGPT help
+# Function which returns Cronbach's alpha
+return_alpha <- function(data, cols) {
+  # select data 
+  selected_data <- data %>% select(all_of(cols))
+  # compute alpha
+  alpha_result <- psych::alpha(selected_data, check.keys = TRUE)
+  # Extract and return the raw alpha value
+  return(alpha_result$total$raw_alpha)
+}
+
+# Creating a list of all measures, grouped by questionnaire
+measures <-
+  list(
+  "Group Malleability" = c("malleable_1", "malleable_2", "malleable_3", "malleable_4"),
+  "Homophily (Appearance)" = c("homophily_appear_1", "homophily_appear_2", "homophily_appear_3", "homophily_appear_4", "homophily_appear_5"),
+  "Homophily (Appearance)" = c("homophily_behave_1", "homophily_behave_2", "homophily_behave_3", "homophily_behave_4", "homophily_behave_6"),
+  "Parasociality" = c("parasocial_1", "parasocial_2", "parasocial_3", "parasocial_4", "parasocial_5"),
+  "Racial Regularities" = c("regularities_1", "regularities_2", "regularities_3", "regularities_4", "regularities_5")
+)
+
+# Creating data frame with measures and corresponding alpha
+reliability <- data.frame(
+  Measure = names(measures),
+  Alpha = sapply(measures, function(cols) return_alpha(youtube, cols))
+)
+
+# Adding column with evaluations of alpha
+reliability <- reliability %>%
+  mutate(Alpha = round(Alpha, digits = 2)) %>% 
+  mutate(
+    Evaluation = case_when(
+      Alpha >= 0.95 ~ "Excellent",
+      Alpha >= 0.9 ~ "Great",
+      Alpha >= 0.8 ~ "Good",
+      Alpha >= 0.7 ~ "Acceptable",
+      Alpha >= 0.6 ~ "Questionable",
+      Alpha < 0.6 ~ "Poor"
+    )
+  )
+
+# Generate table
+kable(reliability, 
+      align = c("c", "c", "c"),
+      # Setting caption here
+      caption = "Reliability (assessed through Cronbach's Alpha) of questionnaires used, within sample") %>% 
+  kable_styling(position = "center", latex_options = c("striped"))
+```
+
+```{r}
+# report regression function
+report_regression <- function(model) {
+
+  # Extract coefficients and p-values
+  m_glance <- glance(model)
+  # Format the p-value
+  p_value <- apa_p(m_glance$p.value, add_equals = TRUE)
+  # Create a string with the results
+  report <- paste0("$F$(", 
+                   m_glance$df, 
+                   ", ", m_glance$df.residual, 
+                   ") = ", round(m_glance$statistic, 2), 
+                   ", $p$ ", p_value,
+                   ", $R^2$ = ", round(m_glance$r.squared, 2))
+  # Return report
+  return(report)    
+}
+```
+
+```{r}
+# report regression coefficients function
+report_coefficients <- function(model){
+  m_tidy <- tidy(model) %>%
+    filter(term != "(Intercept)") %>%
+    mutate(
+      report = paste0(
+        "$B$ = ", round(estimate, 2),
+        ", $SE$ = ", round(std.error, 2),
+        ", $p$ ", apa_p(p.value, add_equals = TRUE)
+      ))
+
+  return(m_tidy$report)
+}
 ```
@@
 # H1: time spent on YouTube and children’s observation of racial regularities covary
+
+# Add age and gender
+
+# Use ptime as primary predictors
+
+lm_h1 <- lm(regularity_score ~ Ptime_max_score + age + gender + race_1, data = youtube)
+summary(lm_h1)
+
+report_regression(lm_h1)
+report_coefficients(lm_h1)
+
+# testing things 
+t.test(regularity_score ~ gender, data = youtube)
+# Male participants only
+t_male <- t.test(youtube$regularity_score[youtube$gender == "Male"], mu = 0.5)
+# Female participants only
+t_female <- t.test(youtube$regularity_score[youtube$gender == "Female"], mu = 0.5)
+t_male
+t_female
+# male scores are significantly different from a neutral score but females are not
+
+ # add age as covariate
+
+ggplot(data = youtube) +
+  aes(x = Ptime_max_score, y = regularity_score) +
+  geom_point() +
+  stat_smooth(method = "lm")
+
+# why is this data so flat?
+# gender, race, state
 ```
@@
 ```{r}
-# H2: if children spend more time on YouTube, they will display greater racial stereotyping and prejudice against outgroups
+# H2: if children spend more time on YouTube, they will display greater racial stereotyping against outgroups
+# Make sure that measure is strongly connected to construct in writing
+
+lm_h2 <- lm(malleable_score ~ Ptime_max_score, data = youtube)
+summary(lm_h2)
+report_regression(lm_h2)
+report_coefficients(lm_h2)
+```
+
+```{r}
+#ns time*gender interaction
+declan_model <- lm(malleable_score ~ Ptime_max_score*gender, data = youtube)
+drop1(declan_model, test = "Chisq")
+#ns time*age interaction
+declan_model2 <- lm(malleable_score ~ Ptime_max_score*age, data = youtube)
+drop1(declan_model2, test = "Chisq")
+#sig predict of gender
+declan_model3 <- glm(malleable_score ~ gender, data = youtube)
+drop1(declan_model3, test = "Chisq")
+
+ggplot(data = youtube) +
+  aes(x = Ptime_score, y = malleable_score) +
+  geom_point() +
+  stat_smooth(method = "loess")
+
+t.test(malleable_score ~ gender, data = youtube)
+t.test(regularity_score ~ gender, data = youtube)
+```
+
+```{r}
+# Genre anovas 
+aov1 <- aov(malleable_score ~ genre, data = youtube)
+summary(aov1)
+
+aov2 <- aov(regularity_score ~ genre, data = youtube)
+summary(aov2)
+
+ggplot(data = youtube) +
+  aes(x = genre) + 
+  geom_bar(color = "black", fill = "grey")
+
 ```
@@
 # H3: the relationship between children’s time spent on YouTube and their exhibited racial stereotyping and prejudice will be mediated by their observations of negative racial regularities
+
+# Add age and gender
+
+lm_h3 <- lm(malleable_score ~ regularity_score, data = youtube)
+summary(lm_h3)
+
+# Mediation model
+# Mediator model (regularity ~ time)
+model.M <- lm(regularity_score ~ Ptime_max_score, data = youtube)
+# Outcome model (malleable ~ time + regularity)
+model.Y <- lm(malleable_score ~ Ptime_max_score + regularity_score, data = youtube)
+med.out <- mediate(model.M, model.Y, treat = "Ptime_max_score", mediator = "regularity_score", boot = TRUE, sims = 1000)
+summary(med.out)
+
+ggplot(data = youtube) +
+  aes(x = regularity_score, y = malleable_score) +
+  geom_point() +
+  stat_smooth(method = "lm")
 ```
@@
 # H4: the relationship between the amount of time that children spend on YouTube and their racial stereotyping and prejudice will be moderated by whether they have a parasocial relationship with a favorite YouTuber of a race other than their own
+
+# If you have a strong relationship with a white youtuber compared to Other - how does this drive racial - most kids put white youtubers as their favorite youtuber, so wanted to see how parasocials with white youtubers are driving the effect
+
+# Add age and gender
+
+lm_h4 <- lm(malleable_score ~ composite, data = youtube)
+summary(lm_h4)
+
+# plotting composite
+ggplot(data = youtube) +
+  aes(x = composite, y = malleable_score) +
+  geom_point() +
+  stat_smooth(method = "lm")
+# plotting each component individually
+ggplot(data = youtube) +
+  aes(x = h_appear_score, y = malleable_score) +
+  geom_point() +
+  stat_smooth(method = "lm")
+ggplot(data = youtube) +
+  aes(x = h_behave_score, y = malleable_score) +
+  geom_point() +
+  stat_smooth(method = "lm")
+ggplot(data = youtube) +
+  aes(x = parasocial_score, y = malleable_score) +
+  geom_point() +
+  stat_smooth(method = "lm")
+
+# controlling for age, effect holds
+
+# effect of genre - check frequencies first, then mean comparisons, then anova (fixed/mixed effects?)
+# race of Youtuber/particular youtuber
 ```
+
+```{r yter race}
+# Favorite YouTuber race
+favorite_coded <- read.csv("favorite_coded.csv")
+
+# Cleaning 
+favorite_youtuber <- inner_join(favorite_coded, youtube, by = join_by(transaction_id)) %>% 
+  rename(yt_gender = Gender) %>% 
+  rename(yt_race = Race.1) %>% 
+  rename(favorite_yt = favorite.x)
+favorite_youtuber <- favorite_youtuber %>% 
+  dplyr::select(favorite_yt, YouTuber, yt_gender, yt_race, gender, race_1, age, Ptime_max_score, malleable_score, regularity_score, h_appear_score, h_behave_score, parasocial_score, composite, race_match_binary)
+
+favorite_youtuber <- favorite_youtuber %>% 
+  mutate(YouTuber = replace_na(YouTuber, "None")) %>% 
+  mutate(yt_match = ifelse(
+    yt_race == race_1,
+    1, 0)) %>% 
+  mutate(yt_match_all = case_when(
+    yt_match == 1 ~ "Match",
+    yt_match == 0 ~ "Mismatch",
+    TRUE ~ "None"
+  )) %>% 
+  mutate(mrbeast = ifelse(
+    YouTuber == "MrBeast",
+    1, 0)) %>% 
+  mutate(yt_white = ifelse(
+    yt_race == "White",
+    1, 0
+  ))
+
+# Mean centering for regression
+favorite_youtuber <- favorite_youtuber %>%
+  mutate(
+    composite_centered = composite - 0.5,
+    regularity_centered = regularity_score - 0.5,
+    malleable_centered = malleable_score - 0.5
+  )
+
+write.csv(favorite_youtuber, "favorite_youtuber.csv")
+```
+
+```{r yter race}
+# Descriptive
+ggplot(data = favorite_youtuber) +
+  aes(x = yt_race) + 
+  geom_bar(color = "black", fill = "grey")
+
+yt_match_mod <- glm(yt_match ~ Ptime_max_score + age + gender, data = favorite_youtuber, family = binomial)
+summary(yt_match_mod)
+
+t.test(Ptime_max_score ~ mrbeast, data = favorite_youtuber) # significant
+t.test(composite ~ mrbeast, data = favorite_youtuber) # not significant
+t.test(malleable_score ~ mrbeast, data = favorite_youtuber) # not significant
+t.test(regularity_score ~ mrbeast, data = favorite_youtuber) # not significant
+# look at subset of mrbeast = fave
+sum(favorite_youtuber$mrbeast) # 42; is power enough? can we make a meaningful comparison with only 42? look into this
+# mr beast is unique sample - not that he's racist in particular, just that this is a pattern that has emerged
+
+# avg age
+# avg time 
+mrbeast_df <- favorite_youtuber %>% 
+  filter(YouTuber == "MrBeast") 
+# time
+mean(mrbeast_df$Ptime_max_score)
+# skewed right
+ggplot(data = mrbeast_df) +
+  aes(x = Ptime_max_score) + 
+  geom_bar(color = "black", fill = "grey")
+# age
+mean(mrbeast_df$age) # mean = 11.2
+ggplot(data = mrbeast_df) +
+  aes(x = age) + 
+  geom_bar(color = "black", fill = "grey")
+# gender
+ggplot(data = mrbeast_df) +
+  aes(x = gender) + 
+  geom_bar(color = "black", fill = "grey")
+
+# do kids who watch all white youtubers show greater prejudice? fixed beliefs? 
+t.test(malleable_score ~ yt_white, data = favorite_youtuber) # not significant
+t.test(regularity_score ~ yt_white, data = favorite_youtuber) # not significant
+```
+
+```{r friend choice}
+# Race and friend choice
+
+# Logistic regression for race match vs no race match - does amount of time on YouTube predict friend choice 
+# then address gender later
+
+logit <- youtube %>% 
+  filter(race_match != 2)
+
+match <- glm(race_match_binary ~ Ptime_max_score + age + gender, data = youtube, family = binomial)
+summary(match)
+
+# Does race match predict malleability, regularity, or composite? 
+match2 <- glm(malleable_score ~ race_match_binary, data = youtube, family = binomial)
+summary(match2)
+match3 <- glm(regularity_score ~ race_match_binary, data = youtube, family = binomial)
+summary(match3)
+match4 <- glm(composite ~ race_match_binary, data = youtube, family = binomial)
+summary(match4)
+
+t.test(malleable_score ~ race_match_binary, data = youtube)
+t.test(regularity_score ~ race_match_binary, data = youtube)
+t.test(composite ~ race_match_binary, data = youtube)
+
+#Do predict malleability, regularity, or composite predict race match? 
+match2 <- glm(race_match_binary ~ malleable_score, data = youtube, family = binomial)
+summary(match2)
+match3 <- glm(race_match_binary ~ regularity_score, data = youtube, family = binomial)
+summary(match3)
+match4 <- glm(race_match_binary ~ composite, data = youtube, family = binomial)
+summary(match4)
+
+ggplot(logit) +
+  aes(x = Ptime_max_score, y = race_match) +
+  geom_point(position = position_jitter(height = 0.05), alpha = 0.5) +
+  geom_smooth(method = "glm", method.args = list(family = "binomial"), 
+              formula = y ~ x, se = TRUE)
+
+binom.test(x = sum(youtube$race_match == 1),
+           n = nrow(youtube),
+           p = 0.5,
+           alternative = "greater")  # Use "two.sided" if you're testing any difference
+
+```
+
+```{r}
+# Exploratory:
+# Parent opinion
+```
+
+```{r}
+library(boot)
+
+# Your data: df
+# Predictors: time_youtube, racial_regularities
+# Outcome: racial_attitudes
+
+# Define bootstrap function
+boot_fn <- function(data, indices) {
+  d <- data[indices, ]  # resample
+  model <- lm(malleable_score ~ Ptime_max_score + regularity_score, data = youtube)
+  return(coef(model)[c("Ptime_max_score", "regularity_score")])
+}
+
+# Run bootstrap
+set.seed(123)
+results <- boot(data = youtube, statistic = boot_fn, R = 1000)
+
+# Extract bootstrap coefficients
+boot_coefs <- results$t  # matrix: rows = bootstraps, columns = coefficients
+
+# Calculate covariance
+cov(boot_coefs[, 1], boot_coefs[, 2])
+```
+
+```{r}
+library(mediation)
+
+model.m <- lm(regularity_score ~ gender, data = youtube)
+model.y <- lm(malleable_score ~ gender + regularity_score, data = youtube)
+
+med_output <- mediate(model.m, model.y, treat = "gender", mediator = "regularity_score", boot = TRUE)
+summary(med.out)
+
+# Extract estimates
+acme   <- round(med.out$d0, 3)
+ade    <- round(med.out$z0, 3)
+total  <- round(med.out$tau.coef, 3)
+propmed <- round(med.out$n0, 2)
+
+# Extract p-values (formatted APA-style)
+acme_p  <- ifelse(med.out$d0.p < .001, "< .001", paste0("= ", round(med.out$d0.p, 3)))
+ade_p   <- ifelse(med.out$z0.p < .001, "< .001", paste0("= ", round(med.out$z0.p, 3)))
+total_p <- ifelse(med.out$tau.p < .001, "< .001", paste0("= ", round(med.out$tau.p, 3)))
+propmed_p <- ifelse(med.out$n0.p < .001, "< .001", paste0("= ", round(med.out$n0.p, 3)))
+
+```
+
+```{r}
+library(DiagrammeR)
+
+grViz(sprintf("
+digraph mediation {
+
+  graph [layout = dot, rankdir = LR]
+
+  node [shape = box, fontsize = 10, width = 1.1, style = solid]
+
+  X [label = 'IV\\n(gender)']
+  M [label = 'Mediator\\n(regularity_score)']
+  Y [label = 'DV\\n(malleable_score)']
+
+  edge [fontsize = 10]
+
+  X -> M [label = 'a = %.3f\\np %s']
+  M -> Y [label = 'b (implied)']
+  X -> Y [label = 'c′ = %.3f\\np %s']
+
+  # Add total and proportion mediated as a note
+  node [shape = plaintext, fontsize = 9]
+  info [label = 'Total effect = %.3f (p %s)\\nProportion mediated = %.2f (p %s)']
+  info -> Y [style = invis]
+}
+", acme, acme_p, ade, ade_p, total, total_p, propmed, propmed_p))
+```
+
+```{r}
+# 1. Group difference only
+t.test(malleable_score ~ gender, data = youtube)
+
+# 2. Simple regression
+a <- lm(malleable_score ~ gender, data = youtube)
+summary(a)
+
+# 3. With racial regularities added
+b <- lm(malleable_score ~ gender + regularity_score, data = youtube)
+summary(b)
+```
+
+```{r}
+# Favorite YouTuber and regularity
+
+# Anova
+anov2 <- aov(regularity_score ~ yt_match_all, data = favorite_youtuber)
+summary(anov2)
+TukeyHSD(anov2)
+
+# Regression
+lrp_centered <- lm(regularity_score ~ yt_match_all * composite_center + malleable_center, data = favorite_youtuber)
+summary(lrp_centered)
+
+# Plot
+ggplot(data = favorite_youtuber) +
+  aes(x = composite, y = regularity_score) +
+  facet_wrap(~ yt_match_all) +
+  stat_smooth(method = "lm", color = "#800000", linewidth = 0.8, fill = "lightgrey") +
+  geom_point() +
+  my_theme()  
+```
+
+```{r}
+# max
+max_time <- youtube %>% 
+  filter(Ptime_max_score > 15)
+
+maxtest <- lm(malleable_score ~ Ptime_max_score, data = youtube)
+summary(maxtest)
+
+maxtest2 <- lm(regularity_score ~ Ptime_max_score, data = youtube)
+summary(maxtest2)
+```
+```{r}
+#| label: fig-youtuber-descriptive
+#| fig-cap: "Distributions of race/ethnicity of participants and their self-reported favorite YouTubers"
+#| layout-ncol: 2
+#| fig-height: 6
+
+# Stacking two plots
+par(mfrow = c(1, 2))
+
+# Plot 1: Distribution of participant race/ethnicity
+ggplot(favorite_youtuber) +
+  aes(x = race_1) +
+  geom_bar(fill = "darkgrey", color = "black") + 
+  scale_y_continuous(breaks = seq(from = 0, to = 90, by = 15),
+                     limits = c(0, 90)) +
+  labs(x = "Race/Ethnicity", y = "Count",
+       title = "Participant Race/Ethnicity") +
+  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
+  my_theme()
+
+# Plot 2: Distribution of favorite youtuber race/ethnicity
+ggplot(favorite_youtuber) +
+  aes(x = yt_race) +
+  geom_bar(fill = "darkgrey", color = "black") + 
+  scale_y_continuous(breaks = seq(from = 0, to = 90, by = 15),
+                     limits = c(0, 90)) +
+  labs(x = "Race/Ethnicity", y = "Count",
+       title = "Race/Ethnicity of Children's Favorite YouTubers") +
+  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
+  my_theme()
+```
+
+```{r}
+# gender
+lm1 <- lm(composite ~ gender, data = favorite_youtuber)
+summary(lm1)
+lm2 <- lm(composite ~ gender + yt_match_all, data = favorite_youtuber)
+summary(lm2)
+lm3 <- lm(composite ~ gender * yt_match_all, data = favorite_youtuber)
+summary(lm3)
+lm4 <- lm(regularity_score ~ gender, data = favorite_youtuber)
+summary(lm4)
+
+combined_model <- lm(malleable_score ~ gender + yt_match_all + composite + regularity_score, data = favorite_youtuber)
+summary(combined_model)
+
+# Gender as mediator
+# Step 1: Mediator model
+med_model1 <- lm(composite ~ gender, data = favorite_youtuber)
+# Step 2: Outcome model (DV predicted by mediator + gender)
+out_model1 <- lm(malleable_score ~ composite + gender, data = favorite_youtuber)
+# Run mediation analysis
+med_out1 <- mediate(med_model1, out_model1, treat = "gender", mediator = "composite", boot = TRUE)
+
+# Mediator model
+med_model2 <- lm(regularity_score ~ gender, data = favorite_youtuber)
+# Outcome model
+out_model2 <- lm(malleable_score ~ regularity_score + gender, data = favorite_youtuber)
+# Mediation
+med_out2 <- mediate(med_model2, out_model2, treat = "gender", mediator = "regularity_score", boot = TRUE)
+
+summary(med_out1)
+summary(med_out2)
+
+```

### 2025-04-14 manuscript.qmd
Updated manuscript draft

@@
     postal-code: 60637
-abstract: "One way in which children learn about group dynamics within their racial world is from patterns in their daily environments.
-The current study seeks to understand the degree to which YouTube, a popular form of social media, exposes children to negatively valenced racial patterns, and potentially affects their beliefs.
-Dyads of parents and 8-13 year-old children (N = 18) describe daily YouTube usage, and the effects of children's YouTube usage are assessed.
-In the present sample, there is no relationship between children's YouTube usage, racial patterns they may observe, and negative racial beliefs."
+abstract: "To what extent might YouTube influence children’s beliefs about racial outgroups?
+Though it is well established that children can learn about group dynamics within their racial world from patterns in their daily environments, the majority of research in this domain has focused on in-person environmental dynamics.
+The current study examines whether YouTube exposes children to negative outgroup behaviors, potentially affecting their beliefs.
+In an online questionnaire, dyads of parents and 8-13 year-old children (N = 200 dyads) described children’s daily YouTube usage.
+We found that time spent on YouTube each week was not associated with increased perception of negative racial patterns on YouTube (B = 0.00, p = .397), nor was time spent on YouTube associated with an increase in prejudice against racial outgroups (B = 0.00, p = .376).
+However, male participants (t = -2.45, p = .029) and participants with higher parasociality scores (B = 0.81, SE = 0.08, p < .001) displayed greater prejudice.
+These findings suggest that prejudice is predicted by more than just online exposure to negative racial patterns; children’s identities and preferences may play a larger role."
 floatsintext: true
@@
     list-of-tables: true
+    toc: true
 editor: visual
@@
 # Necessary libraries
-#install.packages(papaja)
 library(papaja)
-#install.packages(kableExtra)
+library(lm.beta)
+library(citr)
+library(mediation)
 library(kableExtra)
-#install.packages(psych)
 library(psych)
@@
 library(tidyverse)
+
+# R References
+# r_refs(file = "r-references.bib")
 
@@
 youtube <- read_csv("data/youtube.csv", col_names = TRUE)
-
+favorite_youtuber <- read_csv("data/favorite_youtuber.csv", col_names = TRUE)
 ```
@@
 
-Is YouTube making kids more racist?
+Is YouTube making children more racist?
 Despite sounding like the cultural fear-mongering often associated with screen time and development, such a question refers to real concerns that psychological research has yet to address: what are children really learning from YouTube, particularly with regard to race?
@@
 
-This study will examine the relationship between YouTube usage and children’s development of racial attitudes, so as to understand whether and the degree to which YouTube may be a site of ethnic-racial socialization where children develop prejudices against those of other races.
+This study will examine the relationship between YouTube usage and children’s development of racial attitudes, so as to understand whether and the degree to which YouTube may be a site of ethnic-racial socialization where children develop stereotypes regarding those of other races.
 
-I hypothesize that time spent on YouTube and children’s observation of racial regularities should covary; as children spend more time on YouTube, they may observe more negatively valenced racial regularities including people of color [@guoharlow_2014_usergenerated; @rollinsetal_2022_who].
-Thus, I hypothesize that if children spend more time on YouTube, they will display greater racial stereotyping and prejudice against outgroups.
+I hypothesize that time spent on YouTube and children’s observation of racial regularities should covary; as children spend more time on YouTube, they may observe more negatively valenced, stereotypical racial regularities including people of color [@guoharlow_2014_usergenerated; @rollinsetal_2022_who].
+Thus, I hypothesize that if children spend more time on YouTube, they will display more fixed beliefs regarding racial outgroups.
 While some children may not be consciously aware of on-screen racial regularities, these dynamics may still affect their racial attitudes [@hugheswatford_2022_racial].
-As such, I hypothesize that the relationship between children’s time spent on YouTube and their exhibited racial stereotyping and prejudice will be mediated by their observations of negative racial regularities.
+As such, I hypothesize that the relationship between children’s time spent on YouTube and their exhibited racial stereotyping will be mediated by their observations of negative racial regularities.
 
@@
 This theory suggests that when individuals have limited real life interpersonal contact with minority groups, the formation of parasocial (one-sided) relationships with outgroup media figures may reduce stereotyping and prejudice [@schiappaetal_2005_parasocial; @wongetal_2022_theorizing].
-Much of the parasocial contact hypothesis literature explores the prejudice reduction made possible by parasocial relationships with television characters, yet the growing popularity of social media presents another medium through which parasocial relationships may be formed.
+Much of the parasocial contact hypothesis literature explores the prejudice and stereotype reduction made possible by parasocial relationships with television characters, yet the growing popularity of social media presents another medium through which parasocial relationships may be formed.
 If positive parasocial contact hypothesis effects may be observed when individuals form relationships with characters in other media, so too should these effects be observed when individuals have parasocial relationships with outgroup influencers [@banasetal_2020_metaanalysis].
-Thus, I pose my third hypothesis: the relationship between the amount of time that children spend on YouTube and their racial stereotyping and prejudice will be moderated by whether they have a parasocial relationship with a favorite YouTuber of a race other than their own.
-Specifically, if children have a favorite YouTuber of a race other than their own and they have a parasocial relationship with this YouTuber, they will display less racial stereotyping and prejudice.
+Thus, I pose my final hypothesis: the relationship between the amount of time that children spend on YouTube and their racial stereotyping will be moderated by whether they have a parasocial relationship with a favorite YouTuber of a race other than their own.
+Specifically, if children have a favorite YouTuber of a race other than their own and they have a parasocial relationship with this YouTuber, they will display less racial stereotyping.
 
@@
 
-This study includes dyads of parents and children between the ages of 8 and 13 [^1].
+This study includes dyads of parents and children between the ages of 8 and 13 years old.
 Though children may express negative racial attitudes prior to this point in development, during early adolescence, children develop the ability to recognize and reflect on the racial patterns and dynamics present in their environments [@hugheswatford_2022_racial].
@@
 
-[^1]: Pilot data has demonstrated that Qualtrics Panels has not, thus far, been as stringent in participant age verification.
-As such, data used presently is from a broader age range than will be included in the final sample, after stricter age validation has been included.
-
-Pilot data has been collected in March of 2025 from families recruited via Qualtrics Panels (*N* = `r length(youtube$transaction_id)`).
+Data was been collected in March of 2025 from families recruited via Qualtrics Panels.
+`r length(youtube$transaction_id)` dyads were collected; the final sample contained `r length(youtube$transaction_id)` parents and `r length(youtube$transaction_id)` children (*M* = `r round(mean(youtube$age), digits = 1)`, `r sum(youtube$gender == "female")` girls).
 Participating families receive two Qualtrics surveys to be completed asynchronously, and receive compensation (as determined by Qualtrics Panels) after both surveys have been completed.
@@
 
-In the parent survey, participants answer questions related to parent and child demographics (child age, race/ethnicity, parent income and level of education, etc.), as well as questions regarding their child’s YouTube usage (for instance, time spent on YouTube, as reported by their child’s device screen time).
+In the parent survey, participants answered questions related to parent and child demographics (child age, race/ethnicity, parent income and level of education, etc.), as well as questions regarding their child’s YouTube usage (for instance, time spent on YouTube on an average day).
 
-In the child survey, children answer questions related to their YouTube usage, such as time spent on YouTube and their favorite genre.
-Next, they will either answer more questions pertaining to YouTube content, or their general racial attitudes; either block of questions will appear randomly, so as to reduce the influence of question order.
-In the racial attitudes section, children will answer questions regarding outgroup prejudices, as rated on a Likert scale.
-They will also complete one friend choice item, as a simple exploratory measure of racial preference.
-In the YouTube content section, children will be asked to think of their favorite YouTuber as they answer questions related to whether they have a parasocial relationship with that YouTuber, as well as their observations of racial regularities on YouTube.
+In the child survey, children answered questions related to their YouTube usage, such as time spent on YouTube and their favorite genre.
+Next, they either answered more questions pertaining to YouTube content, or their general racial attitudes; either block of questions appeared randomly, so as to reduce order effects.
+In the racial attitudes section, children answered questions regarding outgroup prejudices, as rated on a Likert scale (all coded such that 1 = *Really disagree* and 5 = *Really agree*).
+They also completed one friend choice item, as a measure of racial preference.
+In the YouTube content section, children were asked to think of their favorite YouTuber as they answered questions related to whether they have a parasocial relationship with that YouTuber, as well as their observations of racial regularities on YouTube, as rated on the same Likert scale as in previous questions.
 
-The particular measures used in the child survey are as follows:
+Beliefs about groups, particularly in terms of group malleability, were chosen as the primary outcome measure to assess racial attitudes, stereotyping in particular.
+Such questions, adapted from @halperinetal_2012_promoting, address whether children have fixed or malleable views—stereotypes—regarding outgroups (e.g.
+when prompted to think about groups with different skin colors than their own, children are asked the extent to which they agree with the statement, "These groups of people can't really change the way they act").
+Higher scores in this domain demonstrate more fixed evaluations of outgroup members, suggesting an underlying racial essentialism, or a belief in the intrinsic nature of racial difference [@waxman_2021_racial].
 
-1. Beliefs about groups (adapted from @halperinetal_2012_promoting)
-2. Perceived homophily in behavior and appearance (adapted from @mccroskeyetal_1975_development)
-3. Parasocial interaction with a YouTuber (adapted from @sungetal_2023_shes)
-4. Racial regularities (created based on @rollinsetal_2022_who)
-5. Friend choice (adapted from @amemiyabian_2024_why)
+Time spent on YouTube, reported by parents, is the primary predictor of racial attitudes.
+Parents reported the amount of days their child spends on YouTube in an average week, as well as the amount of time their child spends on YouTube in an average day.
+These answers were combined to create an hours per week score.
+
+Racial regularities, hypothesized to mediate the relationship between time spent on YouTube and children's racial attitudes, were measured using racial regularities questionnaire items created for this study.
+As racial regularities are defined in terms of consistent and repeated racialized patterns in a particular environment [@hugheswatford_2022_racial],  this measure was designed to capture potential behavioral patterns in racial outgroups that may appear on YouTube.
+This measure was created using patterns in YouTube videos as captured in a large-scale content analysis by @rollinsetal_2022_who, and included both positive and negative behaviors.
+Children were asked whether they agreed that people who did not look like them expressed each behavior.
+
+Children's parasocial relationships with YouTubers, a potential moderator in the relationship between time spent on YouTube and negative racial attitudes, was measured using a composite score of two questionnaires: perceived homophily in behavior and appearance (adapted from @mccroskeyetal_1975_development) and parasocial interaction with a YouTuber (adapted from @sungetal_2023_shes).
+After listing and being prompted to think about their favorite YouTuber, in these questionnaires, children indicated the degree to which their favorite YouTuber looks, acts, and thinks like them, as well as whether this YouTuber could be their friend.
+Children also completed a friend choice measure, adapted from @amemiyabian_2024_why; this measure captures children's explicit racial preferences with regard to peers.
 
@@
 
-Beliefs about groups, particularly in terms of group malleability, were chosen as the primary outcome measure to assess racial attitudes.
-Such questions, adapted from @halperinetal_2012_promoting, address whether children have fixed or malleable views regarding outgroups (e.g.
-when prompted to think about groups with different skin colors than their own, children are asked the extent to which they agree with the statement, "These groups of people can't really change the way they act").
-Higher scores in this domain demonstrate more fixed evaluations of outgroup members, suggesting an underlying racial essentialism, or a belief in the intrinsic nature of racial difference [@waxman_2021_racial].
-
-Composite scores have been created for each measure. All analyses have been completed in RStudio [@R-base], primarily within the tidyverse and psych packages (@R-tidyverse; @R-psych).
-
 # Results {#sec-results}
 
-Looking first to the distributions of time spent on YouTube among  participants, just as many children use YouTube every day as (*N* = `r sum(youtube$daily == 'Every Day')`) as those who do not (*N* = `r sum(youtube$daily == 'Not Every Day')`).
-And, as shown in @fig-time-distribution, children who use YouTube every day appear to use YouTube for more time on an average day than children who do not.
-On average, parents report that children spend about `r round(mean(youtube$Ptime), digits = 0)` minutes, or `r round(mean(youtube$Ptime)/60, digits = 0)` hour, on YouTube on an average day.
-Some children, as parents report, watch as much as `r round(max(youtube$Ptime)/60, digits = 0)` hours of YouTube, while others watch only `r round(min(youtube$Ptime)/60, digits = 0)`.
-Children's self-report YouTube usage reflects a similar pattern, as shown in @tbl-frequency: the majority of participants report watching YouTube for 30 minutes to 1 hour each day.
+## Regularities, Attitudes, and Time Spent on YouTube {#sec-h1-3}
 
 ```{r}
-#| label: fig-time-distribution
-#| fig-cap: "Distribution of participants' YouTube watch time"
-#| fig-width: 6
-#| fig-height: 4
+#| label: report-correlation
 
-ggplot(subset(youtube, !is.na(Ctime)), aes(x = Ctime)) + 
-  geom_bar(color = "black", fill = "grey") +
-  facet_grid(~ daily) +
-  scale_x_discrete(labels = c("About 15 minutes a day" = "~ 15 min", "About 30 minutes a day" = "~ 30 min", "About 45 minutes a day" = "~ 45 min", "About 1 hour a day" = "~ 1 hr", "About 1 and 1/2 hours a day" = "~ 1.5 hr", "More than 2 hours a day" = "> 2 hr")) +
-  theme(
-    axis.text.x = element_text(angle = 45, hjust = 1)
-  ) +
-  labs(x = "Time Spent on YouTube (Self-Reported)",
-       y = "Number of Participants",
-       title = "Time Spent on YouTube on an Average Day",
-       subtitle = "Comparing children who use YouTube every day and children who do not") +
-  my_theme()
+report_cor <- function(result) {
+  r <- round(result$estimate, 2)
+  p <- ifelse(result$p.value < .001, "< .001", paste0("= ", round(result$p.value, 3)))
+  ci <- round(result$conf.int, 2)
+
+  paste0("r = ", r, ", 95% CI [", ci[1], ", ", ci[2], "], p ", p)
+}
+```
+
+```{r}
+#| label: correlation-time-reg
+
+cor_tr <- cor.test(youtube$Ptime_max_score, youtube$regularity_score)  
+```
+
+```{r}
+#| label: regression-report-function
+
+# report regression function
+report_regression <- function(model) {
+
+  # Extract coefficients and p-values
+  m_glance <- glance(model)
+  # Format the p-value
+  p_value <- apa_p(m_glance$p.value, add_equals = TRUE)
+  # Create a string with the results
+  report <- paste0("$F$(", 
+                   m_glance$df, 
+                   ", ", m_glance$df.residual, 
+                   ") = ", round(m_glance$statistic, 2), 
+                   ", $p$ ", p_value,
+                   ", $R^2$ = ", round(m_glance$r.squared, 2))
+  # Return report
+  return(report)    
+}
+```
+
+```{r}
+#| label: h1-regressions
+
+# Regressing malleability against time, controlling for regularities and age
+h1 <- lm(malleable_score ~ Ptime_max_score + regularity_score + age + gender, data = youtube)
+
+# Regressing regularities against time, controlling for age
+h1.1 <- lm(regularity_score ~ Ptime_max_score + age + gender, data = youtube)
+```
+
+```{r}
+#| label: report-oneway-ttest
+
+report_onesample <- function(t_result) {
+  t_val <- round(t_result$statistic, 2)
+  df <- round(t_result$parameter, 0)
+  p_val <- t_result$p.value
+  p_str <- ifelse(p_val < .001, "< .001", paste0("= ", sub("^0+", "", format(round(p_val, 3), nsmall = 3))))
+  ci <- round(t_result$conf.int, 2)
+  mean_val <- round(t_result$estimate, 2)
+
+  paste0("*t*(", df, ") = ", t_val, ", *p* ", p_str,
+         ", 95% CI [", ci[1], ", ", ci[2], "], *M* = ", mean_val)
+}
 
@@
 ```{r}
-#| label: generate-frequency-table
+#| label: onesample-ttest
 
-frequency <- round(addmargins(prop.table(table(youtube$Ctime, youtube$daily))), 2)
+# One way t-test of mean regularity score against a neutral average
+onesample <- t.test(youtube$regularity_score, mu = 0.5)
 ```
@@
 ```{r}
-#| label: tbl-frequency
-#| tbl-cap: "YouTube Screen Time Frequency Table"
+#| label: report-mlr-results
 
-kable(frequency, 
-      align = c("c", "c", "c"),
-      # Setting caption here
-      caption = "Proportions of watch times in children who watch YouTube every day vs those who do not") %>% 
-  kable_styling(position = "center", latex_options = c("striped"))
+report_mlr_coefficients <- function(model, predictors) {
+  # Compute standardized coefficients
+  standardized_model <- lm.beta::lm.beta(model)
+  betas <- coef(standardized_model)
+  p_vals <- summary(model)$coefficients[, "Pr(>|t|)"]
+
+  # Clean names (remove backticks, spaces)
+  names(betas) <- gsub("`", "", names(betas))
+  names(p_vals) <- gsub("`", "", names(p_vals))
+
+  # Build APA-style strings
+  apa_results <- sapply(predictors, function(pred) {
+    beta <- round(betas[pred], 2)
+    p <- p_vals[pred]
+    p_formatted <- ifelse(p < .001, "< .001", paste0("= ", sub("^0+", "", format(round(p, 3), nsmall = 3))))
+    paste0("*β* = ", beta, ", *p* ", p_formatted)
+  })
+
+  names(apa_results) <- predictors
+  return(apa_results)
+}
+
+```
+
+To test my first hypothesis that increased time spent on YouTube should generally covary with children's observations of negative racial regularities, I calculated the correlation between children's time spent on YouTube per week and racial regularities scores.
+Time spent on YouTube was not significantly correlated with children's perceptions of racial regularities (`r report_cor(cor_tr)`).
+This lack of relationship was confirmed by regressing regularity scores on time (`r report_regression(h1.1)`); though the overall model is significant, time is not a significant predictor of children's observations of racial regularities (`r report_mlr_coefficients(h1.1, "Ptime_max_score")`).
+The significance of this model comes from the addition of gender (`r report_mlr_coefficients(h1.1, "genderMale")`), added as a control alongside age (`r report_mlr_coefficients(h1.1, "age")`).
+Such controls were added so as to curtail variance, as well as to account for age and gender as potential confounds.
+In the current sample, time spent on YouTube was not correlated nor predictive of children's observation of racial regularities.
+In general, children's observations of racial regularities in YouTube videos were not significantly different from a neutral reference point (`r report_onesample(onesample)`), and there was much variance in scores overall, as shown in @fig-regularities.
+However, some of this variance may be explained by children's gender, whether in terms of gendered usage or content.
+
+```{r}
+#| label: fig-regularities
+#| fig-width: 6
+#| fig-height: 4 
+#| fig-cap: "Relationship between children's per-week YouTube watching and observation of racial regularities"
+
+ggplot(data = youtube) +
+  aes(x = Ptime_max_score, y = regularity_score) +
+  geom_point() +
+  stat_smooth(method = "lm", color = "#800000", alpha = 0.3) +
+  scale_y_continuous(breaks = seq(from = 0, to = 1, by = 0.2)) +
+  labs(
+    x = "Time Spent on YouTube Per Week (Hours)",
+    y = "Observation of Racial Regularities",
+    title = "Time Spent on YouTube and Racial Regularities"
+  ) +
+  my_theme()
+```
+
+It was also hypothesized that as a result of the relationship between time spent on YouTube and racial regularities, children who spend greater time on YouTube will display more negative racial attitudes toward outgroups.
+Regressing racial attitudes against time spent on YouTube, controlling for regularities, age, and gender, time spent on YouTube significantly predicts more fixed racial attitudes (`r report_regression(h1)`).
+However, despite a significant positive association, the effect size of time alone on racial attitudes was low (`r report_mlr_coefficients(h1, "Ptime_max_score")`).
+Racial regularity scores significantly predicted racial attitudes: increases in racial regularity scores were significantly associated with increases in fixedness of racial attitudes (`r report_mlr_coefficients(h1, "regularity_score")`), as shown in @fig-reg-mall-regression.
+As such, though there was no observed relationship between time spent on YouTube and racial regularities, nor did the average participant observe significantly negative racial regularities, racial regularities on YouTube may still play a role in children's racial attitudes.
+Neither age nor gender were significant in this model.
+
+```{r}
+#| label: fig-reg-mall-regression
+#| fig-width: 6
+#| fig-height: 4 
+#| fig-cap: "Correlation Between Racial Regularities Score and Racial Attitudes Score"
+
+ggplot(youtube) +
+  aes(x = regularity_score, y = malleable_score) +
+  stat_smooth(method = "lm", color = "#800000", linewidth = 0.8, fill = "lightgrey") +
+  geom_point() +
+  labs(x = "Observation of Negative Regularities", y = "Fixedness in Racial Attitudes",
+       title = "Attitudes vs. Regularity Scores") +
+  my_theme()
 ```
@@
 ```{r}
-#| label: anova-outputs
+#| label: report-twosample-ttest
 
-# ANOVA: racial regularities score predicted by time spent on YT (categorical self-report)
-aov_reg_ctime <- aov(regularity_score ~ Ctime, data = youtube)
+report_twosample <- function(model) {
+  # Extract test-statistic and p-value
+  t_glance <- glance(model)
+  # Format the p-value
+  p_value <- apa_p(t_glance$p.value, add_equals = TRUE)
+  # Create a string with the results
+  report <- paste0("$t$ = ", round(t_glance$statistic, 2), 
+                   ", $p$ ", p_value)
+  return(report)}
+```
 
-# ANOVA: racial regularities score predicted by perceptions of how often kids see outgroup (categorical)
-aov_reg_outfreq <- aov(regularity_score ~ outgroup_freq, data = youtube)
+```{r}
+#| label: gender-effects-ttests
 
-# ANOVA: racial regularities score predicted by perceptions of how often kids see outgroup (categorical)
-aov_mall_outfreq <- aov(malleable_score ~ outgroup_freq, data = youtube)
+# two sample t tests where H0: μ1 = μ2
+reg_twosample <- t.test(regularity_score ~ gender, data = youtube)
+mall_twosample <- t.test(malleable_score ~ gender, data = youtube)
+
+# two sample t tests where H0: μ1 > μ2
+reg_twosample_alt <- t.test(regularity_score ~ gender, data = youtube, alternative = "less")
+mall_twosample_alt <- t.test(malleable_score ~ gender, data = youtube, alternative = "less")
+```
+
+Though gender did not significantly predict racial attitudes in the previous model (`r report_mlr_coefficients(h1, "genderMale")`), it did significantly predict children's observations of racial regularities (`r report_mlr_coefficients(h1.1, "genderMale")`).
+Considering the strength of the correlation between children's observation of racial attitudes on YouTube and their reported racial attitudes, I examined this discrepancy.
+I conducted two-sample t-tests with racial attitudes and racial regularities: there were significant differences between genders in both reported racial attitudes (`r report_twosample(mall_twosample)`) and racial regularities (`r report_twosample(reg_twosample)`).
+Further, one-sided t-tests revealed that male participants displayed significantly more fixed racial attitudes than female participants (`r report_twosample(mall_twosample_alt)`) as well as significantly more negative racial regularities (`r report_twosample(reg_twosample_alt)`).
+As such, it is clear that in this sample, as shown in @fig-reg-mall-regression-gender, gender affects children's expression of more fixed racial attitudes as well as observations of negative racial regularities on YouTube: a child's gender is associated their racial attitudes insofar as gender predicts children's observation of negative racial regularities, which itself then predicts racial attitudes.
+
+```{r}
+#| label: fig-reg-mall-regression-gender
+#| fig-cap: "Racial attitudes and racial regularity scores, by gender"
+#| fig-width: 6
+#| fig-height: 4
+
+ggplot(youtube) +
+  aes(x = regularity_score, y = malleable_score) +
+  facet_wrap(~ gender) +
+  stat_smooth(method = "lm", color = "#800000", linewidth = 0.8, fill = "lightgrey") +
+  geom_point() +
+  labs(x = "Observation of Negative Regularities", y = "Fixedness in Racial Attitudes",
+       title = "Attitudes vs. Regularity Scores") +
+  my_theme()
+```
+Finally, turning to the friend choice measure as a gauge of racial attitudes, there were no significant differences between children who chose a friend of the same race/ethnicity as their own and children who did not, in terms of racial attitudes, observations of racial regularities, parasocial relationships with YouTubers, nor choice of favorite YouTuber.
+
+## Parasocial Relationships with YouTubers {#sec-h4}
+
+```{r}
+#| label: yt-anova
+
+# anova of mean malleability scores 
+anov1 <- aov(malleable_score ~ yt_match_all, data = favorite_youtuber)
+anov1_hsd <- TukeyHSD(anov1)
+
+anovp <- aov(composite ~ yt_match_all, data = favorite_youtuber)
 ```
@@
 
-Preliminary one-way analysis of variance does not indicate that greater amounts of time spent on YouTube (self-report) is associated with a higher racial regularities score (`r report_anova(aov_reg_ctime)`).
-Similarly, thus far, one-way analysis of variance does not indicate that there is any association between ratings of frequency with which children encounter those of other racial groups and racial regularities scores, (`r report_anova(aov_reg_outfreq)`).
-Further, one-way analysis of variance does not indicate a significant relationship between the primary racial attitudes outcome measure, group malleability, and frequency of seeing racial outgroups on YouTube, (`r report_anova(aov_mall_outfreq)`).
+```{r}
+#| label: tukey-hsd-report-function
+
+report_tukey <- function(tukey_object, comparison, digits = 2, p_digits = 3) {
+  factor_name <- names(tukey_object)[1]
+  results <- tukey_object[[factor_name]]
+
+  if (!comparison %in% rownames(results)) {
+    stop(glue::glue("Comparison '{comparison}' not found in TukeyHSD object."))
+  }
+
+  diff <- round(results[comparison, "diff"], digits)
+  lwr <- round(results[comparison, "lwr"], digits)
+  upr <- round(results[comparison, "upr"], digits)
+  pval <- results[comparison, "p adj"]
+
+  p_string <- if (pval < 0.001) {
+    "p < .001"
+  } else {
+    paste0("p = ", format(round(pval, p_digits), nsmall = p_digits))
+  }
+
+  glue::glue(
+    "{comparison}: M difference = {diff}, 95% CI [{lwr}, {upr}], {p_string}."
+  )
+}
+```
+
+I hypothesized that having a parasocial relationship with a YouTuber of a race other than one's own would moderate the relationship between the amount of time children spent on YouTube and their racial attitudes.
+In the present sample, `r as.character(sum(favorite_youtuber$yt_match_all == "Match"))` children's favorite YouTubers were of a matching race/ethnicity (Match) and `r as.character(sum(favorite_youtuber$yt_match_all == "Mismatch"))` were of a different race/ethnicity (Mismatch).
+`r as.character(sum(favorite_youtuber$yt_match_all == "None"))` children did not specify an identifiable favorite YouTuber (None).
+YouTuber race/ethnicity was coded using publicly available online information, and children's race/ethnicity was reported by parents.
+To test a potential relationship between parasociality, race and ethnicity, and racial attitudes, I first conducted an ANOVA so as to assess whether there were significant differences in racial attitudes between favorite YouTuber types.
+This test revealed that there were significant differences in racial attitudes across favorite YouTuber groups (`r as.character(report_anova(anov1))`).
+A post-hoc Tukey's HSD test showed that racial attitudes in the Mismatch group were significantly different than those of children in the Match group (`r as.character(report_tukey(anov1_hsd, "Mismatch-Match"))`).
+No significant differences were observed between Mismatch and None (`r as.character(report_tukey(anov1_hsd, "None-Mismatch"))`), nor between Match and None (`r as.character(report_tukey(anov1_hsd, "None-Match"))`).
+As such, children with a YouTuber whose race/ethnicity matched their own expressed more fixed racial attitudes than those whose favorite YouTuber was of a race/ethnicity other than their own.
 
 ```{r}
-#| label: regression-models
+#| label: parasocial-regressions
 
-# Regressing malleability against time spent on YouTube (reported by parents)
-lm_mt <- lm(malleable_score ~ Ptime, data = youtube)
+# Effect of YouTuber race match and parasocial relationship on malleability (uncentered)
+lmp <- lm(malleable_score ~ yt_match_all * composite + regularity_score, data = favorite_youtuber)
 
-# Regressing malleability against time spent on YouTube (reported by parents) and whether or not YouTube is used daily
-lm_mtd <- lm(malleable_score ~ Ptime + daily, data = youtube)
+# Effect of YouTuber race match and parasocial relationship on malleability (centered)
+lmp_centered <- lm(malleable_score ~ yt_match_all * composite_centered + regularity_centered + Ptime_max_score * composite_centered, data = favorite_youtuber)
+```
 
-# Regressing malleability against regularity
-lm_mr <- lm(malleable_score ~ regularity_score, data = youtube)
+To better understand the relationship between parasociality with a favorite YouTuber and racial attitudes, I created a regression model with racial attitudes as the outcome.
+This model contained: the race/ethnicity match categorical variable, parasociality score, racial regularities score, and time.
+I also included an interaction between race match and parasociality so as to test my primary hypothesis, as well as an interaction term between parasociality and time, to evaluate how parasociality might change with time spent on YouTube.
+This model was significant overall, and explains much of the variance in racial attitudes in this sample (`r as.character(report_regression(lmp_centered))`).
+Turning now to the results of this model, as displayed in @tbl-parasocial-regression, children's observations of racial regularities (centered around a neutral midpoint of 0.5) remained a strongly positive significant predictor of racial attitudes (`r as.character(report_mlr_coefficients(lmp_centered, "regularity_centered"))`).
+The composite measure for parasocial relationships with one's favorite YouTuber (across appearance, behavior, and perceptions of possible friendship; also centered around a neutral midpoint of 0.5), was also a strongly positive and significant predictor of racial attitudes (`r as.character(report_mlr_coefficients(lmp_centered, "composite_centered"))`).
+Though having a favorite YouTuber of a racial or ethnic group other than one's own (Mismatch) did not itself significantly predict racial attitudes (compared to Match), the interaction effect between Mismatch and composite parasociality was significant (`r as.character(report_mlr_coefficients(lmp_centered, "yt_match_allMismatch:composite_centered"))`).
+Though having a favorite YouTuber of a race other than one's own did not itself predict lower racial attitudes, it attenuates the otherwise positive effect of parasociality with a favorite YouTuber.
+Parasocial relationships with YouTubers were predictive of higher racial regularities overall, but such an effect was moderated by having a favorite YouTuber of a different race or ethnicity than one's own.
+Such an effect may be visualized in @fig-interaction.
+
+```{r}
+#| label: prepping-tble
+
+tidy_lmp <- tidy(lmp_centered)
+
+reg_table <- tidy_lmp %>%
+  mutate(
+    term = case_when(
+      term == "(Intercept)" ~ "Intercept",
+      term == "composite_centered" ~ "Parasociality (centered)",
+      term == "regularity_centered" ~ "Regularity (centered)",
+      term == "yt_match_allMismatch" ~ "Mismatch (vs Match)",
+      term == "yt_match_allNone" ~ "None (vs Match)",
+      term == "Ptime_max_score" ~ "YouTube Time",
+      term == "yt_match_allMismatch:composite_centered" ~ "Parasociality × Mismatch",
+      term == "yt_match_allNone:composite_centered" ~ "Parasociality × None",
+      term == "composite_centered:Ptime_max_score" ~ "Parasociality × YouTube Time",
+      TRUE ~ term  
+    ),
+    p.value = case_when(
+      p.value < .001 ~ "<.001",
+      p.value < .01 ~ "<.01",
+      p.value < .05 ~ "<.05",
+      TRUE ~ as.character(round(p.value, 3)))
+  ) %>%
+  select(term, estimate, std.error, statistic, p.value) %>%
+  rename(
+    Predictor = term,
+    B = estimate,
+    `SE(B)` = std.error,
+    t = statistic,
+    p = p.value
+  ) %>%
+  mutate(across(c(B, `SE(B)`, t), ~round(., 2)))
+
 ```
@@
 ```{r}
-#| label: regression-report-functions
+#| label: tbl-parasocial-regression
+#| tbl-cap: "Regression Predicting Malleable Score (Predictors Centered at 0.5)"
 
-# Taken from apaquarto demo
+kable(reg_table, align = "lcccc") %>% 
+  kable_styling(position = "center", latex_options = c("striped"))
 
-# report_regression takes a lm model object as an argument
-# Returns string of format: "$F$(df, df.residual) = F-value, $p$ = p-value"
-
-report_regression <- function(model) {
-
-  # Extract coefficients and p-values
-  m_glance <- glance(model)
-  # Format the p-value
-  p_value <- apa_p(m_glance$p.value, add_equals = TRUE)
-  # Create a string with the results
-  report <- paste0("$F$(", 
-                   m_glance$df, 
-                   ", ", m_glance$df.residual, 
-                   ") = ", round(m_glance$statistic, 2), 
-                   ", $p$ ", p_value)
-  # Return report
-  return(report)    
-}
 ```
 
-Regressing malleability scores against parent reports of time spent on YouTube, no significant relationship is observed (`r report_regression(lm_mt)`).
-.
-This relationship remains unchanged and similarly insignificant when daily use is added as a predictor (`r report_regression(lm_mtd)`).
-Such relationships, as well as that of regularity score and YouTube usage, may be observed in @fig-malleable and @fig-regularity.
-Based on pilot sample alone, there is not enough data to conduct analyses with regard to the effect of YouTuber on racial attitudes, but the modal favorite YouTuber reported has thus far been `r mode(youtube$favorite)` (*N* = `r sum(youtube$favorite == 'MrBeast')`).
-Preliminary relationships between favorite YouTuber (this YouTuber in particular) as well as malleability and regularity scores may be found in @fig-malleable and @fig-regularity respectively.
+Additionally, in this model, time remains a significant predictor of racial attitudes (`r report_mlr_coefficients(lmp_centered, "Ptime_max_score")`), consistent with previous models.
+Further, there is a significant interaction between time spent on YouTube and parasociality score (`r report_mlr_coefficients(lmp_centered, "composite_centered:Ptime_max_score")`); as time spent on YouTube increases, the effect of parasocial relationships with favorite YouTubers decreases.
 
 ```{r}
-#| label: fig-malleable
-#| fig-cap: "Correlations Between Time Spent On YouTube and Group Malleability Beliefs"
-#| fig-width: 5
-#| fig-height: 2
+#| label: fig-interaction
+#| fig-cap: "Parasocial relationships with YouTubers of in or outgroups and racial attitudes"
+#| fig-width: 7
+#| fig-height: 4
 
-ggplot(data = youtube %>% 
-         # filtering outliers that are too low
-             filter(Ptime > 10)) +
-  aes(x = Ptime, y = malleable_score) +
-  facet_grid(~ daily, scales = "free_x") +
-  stat_smooth(method = "lm", color = "#800000") +
-  geom_point(aes(shape = youtuber)) +
-  scale_shape_manual(values = c("Not MrBeast" = 16, "MrBeast" = 1)) +
-  labs(x = "Time Spent on YouTube (minutes)", y = "Malleability Score",
-       shape = "Favorite YouTuber",
-       title = "Malleability and Time Spent on YouTube",
-       caption = "Note: MrBeast is the modal favorite YouTuber.") +
+ggplot(data = favorite_youtuber) +
+  aes(x = composite, y = malleable_score) +
+  facet_wrap(~ yt_match_all) +
+  stat_smooth(aes(color = yt_match_all), 
+              method = "lm", linewidth = 0.8, fill = "lightgrey") +
+  scale_color_manual(values = c("Match" = "black", "Mismatch" = "#CC8214", "None" = "black")) +
+  geom_point() +
+  guides(color = "none") +
+  labs(x = "Composite Parasociality Score", y = "Fixedness of Racial Beliefs",
+       title = "Favorite YouTubers, Parasociality, and Racial Attitudes",
+       caption = "Note: Interaction between race/ethnicity mismatch and parasociality is significant, as highlighted in yellow.") +
   my_theme()
@@
 ```{r}
-#| label: fig-regularity
-#| fig-cap: "Correlations Between Time Spent On YouTube and Racial Regularities"
-#| fig-width: 5
-#| fig-height: 2
+#| label: exploratory-models
 
-ggplot(data = youtube %>% 
-         # filtering outliers that are too low
-             filter(Ptime > 10)) +
-  aes(x = Ptime, y = regularity_score) +
-  facet_grid(~ daily, scales = "free_x") +
-  stat_smooth(method = "lm", color = "#800000") +
-  geom_point(aes(shape = youtuber)) +
-  scale_shape_manual(values = c("Not MrBeast" = 16, "MrBeast" = 1)) +
-  labs(x = "Time Spent on YouTube (minutes)", y = "Regularity Score",
-       shape = "Favorite YouTuber",
-       title = "Racial Regularities and Time Spent on YouTube",
-       caption = "Note: MrBeast is the modal favorite YouTuber.") +
-  my_theme()
+# FIRST: Gender and composite
+g1 <- lm(composite_centered ~ gender, data = favorite_youtuber)
+
+# SECOND: Gender and race_match
+chi_g_table <- table(favorite_youtuber$yt_match_all, favorite_youtuber$gender)
+chi_g <- chisq.test(chi_g_table)
+
+# THIRD: Gender, composite, and race_match
+g2 <- lm(composite ~ gender + yt_match_all, data = favorite_youtuber)
+
+# FOURTH: Malleability against composite, gender, and race_match
+g3 <- lm(malleable_score ~ composite_centered * gender, data = favorite_youtuber)
+
+# FIFTH: Malleability against regularity, gender, and race_match
+g4 <- lm(malleable_score ~ regularity_centered * gender, data = favorite_youtuber)
+
+# SIXTH: huge model with everything
+small_g <- lm(malleable_score ~ regularity_centered + gender + composite_centered + Ptime_max_score, data = favorite_youtuber)
 ```
 
-Just as there is not yet an observed relationship between time spent on YouTube and racial regularities, so too is there a lack of relationship between regularities scores and malleability scores in the present sample (`r report_regression(lm_mr)`).
-The preliminary relationship between racial regularity and malleability scores within the full sample, as well as preliminary effects of daily YouTube usage and participant race may be found in @fig-reg-v-mall.
+```{r}
+#| label: chi-sq-report-function
+
+report_chisq <- function(chi_result) {
+  # Extract and format values
+  X2 <- round(chi_result$statistic, 2)
+  df <- chi_result$parameter
+  p_value <- apa_p(chi_result$p.value, add_equals = TRUE)
+
+  # Create APA-style string
+  report <- paste0("$\\chi^2$(", df, ") = ", X2, ", $p$ ", p_value)
+
+  return(report)
+}
+
+```
+
+## Exploratory Analysis: Gender Effects {#sec-exploratory}
+
+Considering the previously observed association between gender and racial regularities, I conducted some exploratory analyses so as to determine the degree to which gender may play a role in children's YouTube usage, particularly with regard to favorite YouTuber choice and potential gendered differences in racial attitudes and regularities.
+From previous analyses, it is clear that in more robust models, the effect of gender disappears, despite there being significant gendered differences in children's racial attitudes and observations of racial regularities.
+I wanted to examine this discrepancy further.
+
+First, I examined the degree to which gender might affect parasociality; past research has shown that boys are perhaps more likely to engage in parasocial relationships than girls [@gleasonetal_2017_parasocial].
+In this sample, boys were more likely to express higher parasociality than girls (`r report_regression(g1)`), though the effect size was fairly low.
+Then, as prior one-tailed t-tests have shown that boys are more likely to express observing negative racial regularities as well as more fixed racial attitudes, as well as the moderating effect of having a different YouTuber of a race/ethnicity other than one's own, I conducted a chi-squared test to see the extent to which favorite YouTuber race/ethnicity is related to gender.
+This test revealed that there are significant differences between boys and girls in whether or not their favorite YouTuber is of a race other than their own (`r report_chisq(chi_g)`).
+In @tbl-prop-table, the directionality of this effect may be observed: boys in this sample were more likely to have a favorite YouTuber of the same race as their own, while girls did not.
 
 ```{r}
-#| label: fig-reg-v-mall
-#| fig-cap: "Correlation Between Racial Regularities Score and Malleability Score"
-#| fig-subcap: ["Full Sample", "Effects of daily use and participant race"]
-#| layout-ncol: 2
-#| fig-height: 6
+#| label: prep-prop-tble
 
-# Arrange plots (chatgpt rendering assistance)
-par(mfrow = c(1, 2))
+prop_table <- prop.table(chi_g_table)
 
-# Plot 1: Full sample
-ggplot(youtube) +
-  aes(x = regularity_score, y = malleable_score) +
-  stat_smooth(method = "lm", color = "#800000", linewidth = 0.8, fill = "lightgrey") +
-  geom_point() +
-  labs(x = "Regularities Score", y = "Malleability Score",
-       title = "Malleability vs. Regularity Scores") +
-  theme(plot.title = element_text(size = 20), 
-            axis.text = element_text(size = 16),
-            axis.title = element_text(size = 18)) +
-  my_theme()
+# Convert to data frame for kable
+prop_df <- as.data.frame.matrix(round(prop_table, 3))  
+prop_df <- prop_df[, c(ncol(prop_df), 1:(ncol(prop_df)-1))]
+```
 
-# Plot 2: Faceted plot
-ggplot(youtube) +
-  aes(x = regularity_score, y = malleable_score) +
-  stat_smooth(method = "lm", color = "black", linewidth = 0.8, fill = "lightgrey") +
-  geom_point(aes(color = race)) +
-  scale_color_manual(values = c("#155F83", "#C16622")) +
-  facet_wrap(~ daily) +
-  labs(x = "Regularities Score", y = "Malleability Score",
-       color = "Participant Race",
-       title = "Malleability vs. Regularity Scores",
-       caption = "Note: Participant race coded as White/Non-White for pilot data only.") +
-  theme(legend.position = "bottom",
-        plot.title = element_text(size = 20), 
-        axis.text = element_text(size = 16),
-        axis.title = element_text(size = 18), 
-        legend.title = element_text(size = 18),
-        legend.text = element_text(size = 16),
-        plot.caption = element_text(size = 14)) +
-  my_theme()
+```{r}
+#| label: tbl-prop-table
+#| tbl-cap: "Proportions of Favorite YouTuber Race/Ethnicity Match by Gender"
+
+# Print APA-style table
+kable(prop_df, align = "c") %>% 
+  kable_styling(position = "center", latex_options = c("striped"))
+
 ```
+
+As there is a significant relationship between gender and favorite YouTuber race match, a significant relationship between gender and parasociality, as well as previously observed interaction effects between parasociality and YouTuber race match, I created a model with all three variables: I regressed parasociality against gender and the YouTuber race match groups, so as to see the extent to which each independently predicted parasociality.
+The overall model was significant (`r report_regression(g2)`); gender significantly predicted parasociality (`r report_mlr_coefficients(g2, "genderMale")`), as did having a favorite YouTuber of a race other than one's own (`r report_mlr_coefficients(g2, "yt_match_allMismatch")`).
+
+Thus far, in the present sample, there were significant gender differences in racial attitudes and observation of racial regularities, and gender was significantly associated with children's parasociality as well as whether or not their favorite YouTuber was of a race other than their own.
+As such, I then tested the degree to which gender effects hold in more complex models.
+I regressed racial attitudes against parasociality and gender, as well as the interaction effect between parasociality and gender.
+This model is strongly significant (`r report_regression(g3)`), as are the individual effects of parasociality (`r report_mlr_coefficients(g3, "composite_centered")`), gender (`r report_mlr_coefficients(g3, "genderMale")`), and the interaction effect (`r report_mlr_coefficients(g3, "composite_centered:genderMale")`).
+However, regressing racial regularities against parasociality and gender, as well as the interaction effect, though the overall model is significant (`r report_regression(g4)`), only racial regularities remain significant.
+This seemed unusual due to the previously observed gendered differences in racial regularities.
+
+Lastly, I created a complete model regressing racial attitudes against parasociality, racial regularities, gender, and gender.
+Here, the overall model was highly significant (`r report_regression(small_g)`).
+Parasociality (`r report_mlr_coefficients(small_g, "composite_centered")`) and observations of racial regularities (`r report_mlr_coefficients(small_g, "regularity_centered")`) remained significant predictors of racial attitudes, which is consistent with previous models.
+As has occurred in previous models, gender was no longer a significant predictor of racial attitudes (`r report_mlr_coefficients(small_g, "genderMale")`).
+These exploratory analyses of the potential effect of gender show that there is no direct effect of gender on racial attitudes; rather, there are potential *indirect* effects of gender on racial attitudes through gender's influence on YouTube usage.
 
@@
 
-The present study examines the relationship between children's YouTube usage and potential effects on racial attitudes.
-No significant effects of YouTube usage on group beliefs have been observed thus far; within the present study, we thus fail to reject the null hypothesis that there is no difference in racial beliefs between children who spend a lot of time on YouTube and those who do not.
-Similarly, as there is no significant relationship between time spent on YouTube and children's observation of racial regularities, nor between racial regularities and group malleability beliefs, there is no evidence thus far to suggest that observation of racial regularities affects outgroup prejudices as a result of YouTube usage.
+I hypothesized a mediation model for the relationship between time children spend on YouTube and their corresponding racial attitudes.
+In this hypothesis, time spent on YouTube predicts greater observations of negative racial regularities, thus predicting greater stereotyping of members of racial or ethnic outgroups.
+Though children's observations of negative racial regularities on YouTube significantly predicted racial attitudes in this study, time spent on YouTube did not significantly predict these observations.
+Rather, time spent on YouTube significantly predicted racial attitudes in models that otherwise controlled for racial regularities: in such cases, time spent on YouTube was positively associated with more fixed racial attitudes.
 
-Though no relationships have been observed thus far, the present sample is limited in size.
-There is still potential that relationships between YouTube usage, children's observations of racial regularities, and children's expression of group malleability beliefs may emerge in the full sample.
-Further, there is possibility that with the full sample, there is greater evidence for the effect of parasociality.
-Should the full sample yield such results, this would suggest that YouTube is indeed a site of racial socialization for children.
-As it is still currently unknown whether racial regularities are transmitted via social media platforms in a manner that leads to negative attitudes, and this study will be a first step toward understanding such an impact.
-Additionally, if in the full sample if there are significant differences in racial stereotyping and prejudice based on a favorite YouTuber, this would indicate YouTubers as potential points of intervention in a child’s development of racial attitudes and behaviors.
+The lack of relationship between time spent on YouTube and children's observation of negative racial regularities on YouTube suggests that children are not consuming content that is overtly negative on average; spending more time on YouTube will not necessarily expose one to more negative racial characterizations.
+The strong relationship between regularities and attitudes suggests several possibilities: a) children who report seeing more negative racial regularities on YouTube tend to develop more fixed racial attitudes, b) children who observe more negative regularities do so as a result of their fixed attitudes, and c) some third variable, such as prejudice or familial beliefs, both prime children to notice racial regularities and inculcate more fixed attitudes.
+The modest relationship between time spent on YouTube and fixed racial attitudes suggests that may be some other underlying mechanism—perhaps the way the content is presented on YouTube or a cognitive mechanism—contributing to this relationship.
+Or, it may be the case that having more fixed beliefs predisposes children to spending more time on YouTube, as opposed to other media or activities.
 
-Considering the dearth of research on how social media platforms affect children’s racial attitudes and behaviors, this study will provide insights into the extent to which various aspects of social media usage contribute to racial socialization.
-With the future, full sample, findings may still lead to novel discoveries and interventions in the development of negative racial attitudes and behavior.
+Though racial regularities may not mediate the relationship between children's time spent on YouTube and their stereotyping with regard to racial outgroups, children's relationships with their favorite YouTubers play a role.
+I hypothesized that the relationship between time on YouTube and racial attitudes would be moderated by having a parasocial relationship with a favorite YouTuber: if children who spend more time on YouTube develop more fixed racial attitudes regarding outgroups, having a favorite YouTuber of a race other than their own may attenuate such an effect.
+In general, having a parasocial relationship with a YouTuber strongly and significantly predicted more fixed racial attitudes.
+However, having a favorite YouTuber of a race other than one's own significantly decreased this effect.
+Further, spending more time on YouTube significantly decreased the effect of parasociality on racial attitudes.
+
+Considering the overall positive effect of parasociality on fixed racial attitudes, one might assume that spending more time on YouTube would augment such an effect, especially as time spent on YouTube is generally positively correlated with more fixed racial attitudes.
+This discrepancy suggests that as children spend more time on YouTube, they are potentially exposed to more content beyond that of their favorite YouTuber.
+Even if a child has a strong parasocial relationship with their favorite YouTuber, and such a relationship predicts more fixed racial attitudes, no YouTuber's content is exhaustive: with greater time spent on YouTube in an average week, one is likely exposed to other content as that of their favorite has been completely consumed.
+
+## Limitations and Future Research {#sec-limitations}
+
+One limitation of the present study is that there are many underlying or unobserved factors of children's YouTube diets.
+Though some details, such as favorite YouTuber, was recorded, it remains unclear the more specific patterns in YouTube videos children watch.
+Considering the effect of time on attitudes and the effect of noticing regularities on attitudes, knowing exactly what children watch each day (particularly amongst children that watch many hours of YouTube each day) would allow future studies to more clearly parse how specific content patterns contribute to a child's evaluations of outgroups.
+
+Further, as this study was conducted online and asynchronously, I was unable to capture more qualitative data or cognitive mechanisms that could perhaps clarify why children attend to racial regularities in YouTube videos.
+Questions were standardized and multiple choice so as to reduce participant misunderstanding, at the expense of richer data.
+Interview-based data or more open-ended questions could allow future researchers to gain a better understanding of not only what children are seeing, but how such content is evaluated.
+
+Lastly, as this is a correlational study, I am unable to make causal claims regarding the relationship between YouTube usage and racial attitudes.
+As discussed, pre-existing racial attitudes may themselves contribute to a child's observation of racial regularities, as well as who their favorite YouTuber is.
+Longitudinal studies or randomized controlled trials of YouTube diets may allow future researchers to understand the causal direction of the relationships observed in this study.
+
+Considering the dearth of research on how social media platforms affect children’s racial attitudes and behaviors, this study provides insights into the extent to which various aspects of social media usage contribute to racial socialization, and highlights key avenues for future research.
 

### 2025-04-17 manuscript.qmd
added docx

@@
       # Setting caption here
-      caption = "Reliability (assessed through Cronbach's Alpha) of questionnaires used, within sample") %>% 
-  kable_styling(position = "center", latex_options = c("striped"))
+      caption = "Reliability (assessed through Cronbach's Alpha) of questionnaires used, within sample") #%>% 
+  #kable_styling(position = "center", latex_options = c("striped"))
 
@@
 ```
+
 Finally, turning to the friend choice measure as a gauge of racial attitudes, there were no significant differences between children who chose a friend of the same race/ethnicity as their own and children who did not, in terms of racial attitudes, observations of racial regularities, parasocial relationships with YouTubers, nor choice of favorite YouTuber.
@@
 
-kable(reg_table, align = "lcccc") %>% 
-  kable_styling(position = "center", latex_options = c("striped"))
+kable(reg_table, align = "lcccc") #%>% 
+  #kable_styling(position = "center", latex_options = c("striped"))
 
@@
 # Print APA-style table
-kable(prop_df, align = "c") %>% 
-  kable_styling(position = "center", latex_options = c("striped"))
+kable(prop_df, align = "c") #%>% 
+  #kable_styling(position = "center", latex_options = c("striped"))
 
@@
 \clearpage
+
 # References
-:::{refs}
+
+::: {refs}
 :::
